---
title: "Dataset 12"
author: 
output:
  html_document: 
    toc: yes
    number_sections: yes
editor_options: 
  chunk_output_type: inline
---


```{r setup, include=FALSE}
library(psych)
library(relativeVariability)
library(brms)
library(cmdstanr)
library(data.table)
library(ggplot2)
library(dplyr)
library(haven)
library(remotes)
library(loo)
library(knitr)
library(rstan)
library(shinystan)


tb <- read_spss(("~/rstudio01/Neu/Wright/tbuch_days_scales.sav"))
tb_scale <- read_spss(("~/rstudio01/Neu/Wright/tbuch_scales.sav"))

tb_days <- read_spss(("~/rstudio01/Neu/Wright/tbuch_days_items.sav"))
ffm <- read.csv("~/rstudio01/Neu/Wright/ffm1.csv", header=TRUE, sep = ";")

gender <- select(tb_scale, 1, 5)
colnames(gender)[1] <- "id"

colnames(tb)[2] <- "id"
daily_w <- merge(tb, ffm, all.x = T, by= "id")
daily_w <- merge(daily_w, gender, all.x = T, by= "id")
                   
                   
# nur personen mit mehr als 20 Einträgen 
id <- names(which(table(tb_days$vp_id2)>20))

daily_w <- daily_w %>% group_by(id) %>% filter(n()>= 5) %>% ungroup()


colnames(tb_scale)
colnames(tb)
colnames(ffm)
mean(tb_scale$vp_age)
```

# Data Preparation

#Plot NA

```{r}
ggplot(daily_w, aes(panas_n)) +
  geom_histogram(binwidth = 0.1) + 
  ggtitle("Distribution of Negative Emotion Study 12") +
  xlab("Negative Emotion") + ylab("Frequency") + 
  scale_x_continuous(breaks = seq(1, 5, 1)) +
  scale_y_continuous(breaks = seq(0, 4000, 500)) +
  theme(text = element_text(size = 10, family = "Times New Roman"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black")) +
  coord_cartesian(xlim = c(1, 5), ylim = c(0, 4000))

ggsave("NAS12.png", width = 4, height = 3)
```

#PLotPA

```{r}
ggplot(daily_w, aes(panas_p)) +
  geom_histogram(binwidth = 0.1) + 
  ggtitle("Distribution of Negative Emotion Study 12") +
  xlab("Positive Emotion") + ylab("Frequency") + 
  scale_x_continuous(breaks = seq(1, 5, 1)) +
  scale_y_continuous(breaks = seq(0, 1500, 200)) +
  theme(text = element_text(size = 10, family = "Times New Roman"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black")) +
  coord_cartesian(xlim = c(1, 5), ylim = c(0, 1500))

ggsave("PAS12.png", width = 4, height = 3)
```

## Censoring 

```{r}
daily_w$Acens <- case_when(daily_w$panas_n == 1 ~ "left",
                         daily_w$panas_n == 5 ~ "right",
                         TRUE ~ "none")
table(daily_w$Acens)

daily_w$Acens_p <- case_when(daily_w$panas_p == 1 ~ "left",
                         daily_w$panas_p == 5 ~ "right",
                         TRUE ~ "none")
table(daily_w$Acens_p)

mean(daily_w$panas_n)
mean(daily_w$panas_p)
mean(daily_w$neuro, na.rm=T)
sd(daily_w$neuro, na.rm=T)


range(daily_w$panas_p)
```

# BCLSM Negative Emotion

```{r message=TRUE, warning=TRUE}

wn_model_neuro3 <- brm(bf(panas_n | cens(Acens) ~ neuro+ (1|id),
                       sigma ~ neuro  + (1|id)), data = daily_w,
                       iter = 7000, warmup = 2000,chains = 4, init = 0.1,
                   file = "wn_model_neuro3")
print(wn_model_neuro3)
plot(wn_model_neuro3)
prior_summary(wn_model_neuro3)


#posterior_summary(wn_model_neuro3)


```

## Model comparison 
### scale vs. no scale parameter

```{r message=TRUE, warning=TRUE}

wn_model_neuro2 <- brm(panas_n | cens(Acens) ~ neuro + (1|id), data = daily_w,
                    iter = 2000, warmup = 1000,
                   file = "wn_model_neuro2")
print(wn_model_neuro2)
plot(wn_model_neuro2)

modelA <- wn_model_neuro2
modelB <- wn_model_neuro3

modelA <- add_criterion(modelA, "loo")
modelB <- add_criterion(modelB, "loo")

loo <- loo_compare(modelA,modelB, criterion = "loo")

loo <- as.data.frame(loo)

loo$Dataset <- "12"
loo <- tibble::rownames_to_column(loo, "model")

library("writexl")
write_xlsx(loo,"~/looDataset12.xlsx")

kable(loo)
```

### censoring vs. no censoring 

```{r}
wn_model_neuro4 <- brm(bf(panas_n ~ neuro+ (1|id),
                       sigma ~ neuro  + (1|id)), data = daily_w,
                       iter = 7000, warmup = 2000,chains = 4, init = 0.1,
                   file = "wn_model_neuro4")

print(wn_model_neuro4)
```

```{r}

extract_param <- function(model, parameter) {
  ci <- posterior_summary(model, variable = parameter)
  est <- sprintf("%.2f %.2f [%.2f;%.2f]", ci[,"Estimate"],ci[,"Est.Error"], ci[,"Q2.5"], ci[,"Q97.5"])
  est
}

results_Cens<- data.frame(matrix(nrow = 2, # Modelle & RVI 
                             ncol = 6+1)) # 2 Affekte a 3 Spalten 
names(results_Cens) <- c("model", "negemo_b_neuro", "negemo_b_neuro_sigma", "negemo_sigma",
                    "posemo_b_neuro", "posemo_b_neuro_sigma", "posemo_sigma"
                    )

results_Cens$model <- c("modelCensoring", "modelnoCensoring")

#NA

results_Cens[1, "negemo_b_neuro"] <- extract_param(wn_model_neuro3, "b_neuro")
results_Cens[1, "negemo_b_neuro_sigma"] <- extract_param(wn_model_neuro3, "b_sigma_neuro")
results_Cens[1, "negemo_sigma"] <- extract_param(wn_model_neuro3, "b_sigma_Intercept")

results_Cens[2, "negemo_b_neuro"] <- extract_param(wn_model_neuro4, "b_neuro")
results_Cens[2, "negemo_b_neuro_sigma"] <- extract_param(wn_model_neuro4, "b_sigma_neuro")
results_Cens[2, "negemo_sigma"] <- extract_param(wn_model_neuro4, "b_sigma_Intercept")

```


### BCLSM vs. model C (two-part model)

```{r silent=2, comment=F, error=FALSE}
daily_w <- daily_w %>% left_join(daily_w %>% distinct(id, neuro) %>% mutate(neuro_Q =Hmisc::cut2(neuro, g = 4)), by = c("id", "neuro"))



wn_model_neuro_modelC <- brm(bf(panas_n | cens(Acens) ~ neuro + (1|gr(id, by = neuro_Q)),
                  sigma ~ neuro + (1|id)), data = daily_w,
                  iter = 5000, warmup = 2000,  chains = 4,
                  control = list(adapt_delta = .95), init = 0.1,
                  file = "wn_model_neuro_modelC")


print(wn_model_neuro_modelC)
```

```{r}
modelB <- wn_model_neuro3
modelC <- wn_model_neuro_modelC

modelB <- add_criterion(modelB, "loo")
modelC <- add_criterion(modelC, "loo")

loo_c <- loo_compare(modelB,modelC, criterion = "loo")

loo_c <- as.data.frame(loo_c)

loo_c$Dataset <- "12"
loo_c <- tibble::rownames_to_column(loo_c, "model")

library("writexl")
write_xlsx(loo_c,paste0("loo_c12",".xlsx"))

kable(loo_c)
```

## control for gender  

```{r}
daily_w$vp_female <-  as.factor(daily_w$vp_female)

wn_model_sex <- brm(bf(panas_n | cens(Acens) ~ neuro + vp_female + (1|id),
                       sigma ~ neuro +  vp_female + (1|id)), data = daily_w,
                       iter = 2000, warmup = 1000,
                   file = "wn_model_sex")
print(wn_model_sex)
plot(wn_model_sex)

prior_summary(wn_model_sex)
```

# BCLSM Positive Emotion

```{r message=TRUE, warning=TRUE}
wp_model_neuro3 <- brm(bf(panas_p | cens(Acens_p) ~ neuro + (1|id),
                       sigma ~ neuro + (1|id)), data = daily_w,
                      control = list(adapt_delta = .99),
                       iter = 2000, warmup = 1000,
                   file = "wp_model_neuro3")
print(wp_model_neuro3)
plot(wp_model_neuro3)

prior_summary(wp_model_neuro3)
pp_check(wp_model_neuro3)

```

## Model comparison 
### scale vs. no scale parameter

```{r}
wp_model_neuro2 <- brm(panas_p | cens(Acens_p) ~ neuro + (1|id), data = daily_w,
                    iter = 2000, warmup = 1000,
                   file = "wp_model_neuro2")
print(wp_model_neuro2)
```


```{r}
modelAp <- wp_model_neuro2
modelBp <- wp_model_neuro3


modelAp <- add_criterion(modelAp, "loo")
modelBp <- add_criterion(modelBp, "loo")


looP <- loo_compare(modelAp,modelBp, criterion = "loo")

looP <- as.data.frame(looP)

looP$Dataset <- "12"
looP <- tibble::rownames_to_column(looP, "model")
library("writexl")
write_xlsx(looP,"~/looPDataset12.xlsx")

kable(looP)
```


### censoring vs. no censoring 

```{r}
wp_model_neuro4 <- brm(bf(panas_p  ~ neuro + (1|id),
                       sigma ~ neuro + (1|id)), data = daily_w,
                      control = list(adapt_delta = .99),
                       iter = 2000, warmup = 1000,
                   file = "wp_model_neuro4")

print(wp_model_neuro4)
```

```{r}
results_Cens[1, "posemo_b_neuro"] <- extract_param(wp_model_neuro3, "b_neuro")
results_Cens[1, "posemo_b_neuro_sigma"] <- extract_param(wp_model_neuro3, "b_sigma_neuro")
results_Cens[1, "posemo_sigma"] <- extract_param(wp_model_neuro3, "b_sigma_Intercept")

results_Cens[2, "posemo_b_neuro"] <- extract_param(wp_model_neuro4, "b_neuro")
results_Cens[2, "posemo_b_neuro_sigma"] <- extract_param(wp_model_neuro4, "b_sigma_neuro")
results_Cens[2, "posemo_sigma"] <- extract_param(wp_model_neuro4, "b_sigma_Intercept")
```

### BCLSM vs. model C (two-part model)

```{r}
wp_model_neuro_modelC <- brm(bf(panas_p | cens(Acens) ~ neuro + (1|gr(id, by = neuro_Q)),
     sigma ~ neuro + (1|id)), data = daily_w,
  iter = 5000, warmup = 2000,  chains = 4,
  control = list(adapt_delta = .95), init = 0.1,
                   file = "wn_model_neuro_modelC")


print(wp_model_neuro_modelC)
```

```{r}
modelB <- wp_model_neuro3
modelC <- wp_model_neuro_modelC

modelB <- add_criterion(modelB, "loo")
modelC <- add_criterion(modelC, "loo")

loo_cP <- loo_compare(modelB,modelC, criterion = "loo")

loo_cP <- as.data.frame(loo_cP)

loo_cP$Dataset <- "12"
#loo_cP <- tibble::rownames_to_column(loo_c, "model")
library("writexl")
write_xlsx(loo_cP,paste0("loo_cP12", ".xlsx"))

kable(loo_cP)
```




```{r}
extract_param <- function(model, parameter) {
  ci <- posterior_summary(model, variable = parameter)
  est <- sprintf("%.2f %.2f [%.2f;%.2f]", ci[,"Estimate"],ci[,"Est.Error"], ci[,"Q2.5"], ci[,"Q97.5"])
  est
}

results_wd <- data.frame(matrix(nrow = 7, # Modelle & RVI 
                             ncol = 8+1)) # 2 Affekte a 3 Spalten 
names(results_wd) <- c("model", "negemo_b_neuro", "negemo_b_neuro_sigma", "negemo_sigma", "b_neg_sigma_sex",
                    "posemo_b_neuro", "posemo_b_neuro_sigma", "posemo_sigma", "b_pos_sigma_sex"
                    )

results_wd$model <- c("model1", "model2", "model3",
                  "RSD", "RSD_weight", "SD", "gender")


#NA

results_wd[2, "negemo_b_neuro"] <- extract_param(wn_model_neuro2, "b_neuro")
results_wd[2, "negemo_sigma"] <- extract_param(wn_model_neuro2, "sigma")

results_wd[3, "negemo_b_neuro"] <- extract_param(wn_model_neuro3, "b_neuro")
results_wd[3, "negemo_b_neuro_sigma"] <- extract_param(wn_model_neuro3, "b_sigma_neuro")
results_wd[3, "negemo_sigma"] <- extract_param(wn_model_neuro3, "b_sigma_Intercept")

#gender

results_wd[7, "negemo_b_neuro"] <- extract_param(wn_model_sex, "b_neuro")
results_wd[7, "negemo_b_neuro_sigma"] <- extract_param(wn_model_sex, "b_sigma_neuro")
results_wd[7, "negemo_sigma"] <- extract_param(wn_model_sex, "b_sigma_Intercept")
results_wd[7, "b_neg_sigma_sex"] <- extract_param(wn_model_sex, "b_sigma_vp_female1")

#pa

results_wd[2, "posemo_b_neuro"] <- extract_param(wp_model_neuro2, "b_neuro")
results_wd[2, "posemo_sigma"] <- extract_param(wp_model_neuro2, "sigma")

results_wd[3, "posemo_b_neuro"] <- extract_param(wp_model_neuro3, "b_neuro")
results_wd[3, "posemo_b_neuro_sigma"] <- extract_param(wp_model_neuro3, "b_sigma_neuro")
results_wd[3, "posemo_sigma"] <- extract_param(wp_model_neuro3, "b_sigma_Intercept")

```

# RVI (Relative-Variability-Index)
## Unweighted RVI

```{r message=TRUE, warning=TRUE}

ffm$RSD_NA <- NA
for (i in 1:nrow(ffm)) {
  # aktuelle Zeilennummer
  if (ffm$id[i] %in% daily_w$id) {
    if (
      sum(!is.na(daily_w$panas_n[daily_w$id == ffm$id[i]])) >= 5
    ) { 
      ffm$RSD_NA[i] <- relativeSD(daily_w$panas_n[daily_w$id == ffm$id[i]],
                                     1, 5)
    }
  } 
}

range(ffm$RSD_NA, na.rm=T)

ffm$logrsd_n <- log(ffm$RSD_NA)

w_rvi_na <- brm(logrsd_n ~ neuro, data= ffm,
                 file = "wn_logrsd_uw")

results_wd[4,3] <- extract_param(w_rvi_na, "b_neuro")




ffm$RSD_PA <- NA
for (i in 1:nrow(ffm)) {
  # aktuelle Zeilennummer
  if (ffm$id[i] %in% daily_w$id) {
    if (
      sum(!is.na(daily_w$panas_p[daily_w$id == ffm$id[i]])) >= 5
    ) { 
      ffm$RSD_PA[i] <- relativeSD(daily_w$panas_p[daily_w$id == ffm$id[i]],
                                     1, 5)
    }
  } 
}

range(ffm$RSD_PA)

ffm$logrsd_p <- log(ffm$RSD_PA)

w_rvi_pa <- brm(logrsd_p ~ neuro, data= ffm,
                 file = "wp_logrsd_uw")
print(w_rvi_pa)
results_wd[4,6] <- extract_param(w_rvi_pa, "b_neuro")

```


## Weighted RVI 

```{r message=TRUE, warning=TRUE}
ffm$mean_NA <- NA
for (i in 1:nrow(ffm)) {
  if (ffm$id[i] %in% daily_w$id) {
    if (
      sum(!is.na(daily_w$panas_n[daily_w$id == ffm$id[i]])) >= 5
    ) { 
      ffm$mean_NA[i] <- mean(daily_w$panas_n[daily_w$id == ffm$id[i]],
                                   na.rm = T)
    }
  } 
}


ffm$mean_PA <- NA
for (i in 1:nrow(ffm)) {
  if (ffm$id[i] %in% daily_w$id) {
    if (
      sum(!is.na(daily_w$panas_p[daily_w$id == ffm$id[i]])) >= 5
    ) { 
      ffm$mean_PA[i] <- mean(daily_w$panas_p[daily_w$id == ffm$id[i]],
                                   na.rm = T)
    }
  } 
}
```


```{r message=TRUE, warning=TRUE}

ffm$weight_NA <- NA
for (i in 1:nrow(ffm)) {
  if (ffm$id[i] %in% daily_w$id) {
  
    
    if (!is.na(ffm$mean_NA[i])) {
      # Wenn mean nicht fehlt
      ffm$weight_NA[i] <- maximumSD(ffm$mean_NA[i], # Mittelwert
                                       1,  # Minimum
                                       5,  # Maximum
                                       sum(!is.na(daily_w$panas_n[daily_w$id == ffm$id[i]])) 
      ) 
      # W as reported in paper
      ffm$weight_NA[i] <- ffm$weight_NA[i]^2
    }
  }
}

w_rvi_na_w <- brm(logrsd_n|weights(weight_NA) ~ neuro, data= ffm,
                   file = "wn_logrsd_w")
print(w_rvi_na_w)
results_wd[5,3] <- extract_param(w_rvi_na_w, "b_neuro")



ffm$weight_PA <- NA
for (i in 1:nrow(ffm)) {
  if (ffm$id[i] %in% daily_w$id) {
  
    
    if (!is.na(ffm$mean_PA[i])) {
      # Wenn mean nicht fehlt
      ffm$weight_PA[i] <- maximumSD(ffm$mean_PA[i], # Mittelwert
                                       1,  # Minimum
                                       5,  # Maximum
                                       sum(!is.na(daily_w$panas_p[daily_w$id == ffm$id[i]])) 
      ) 
      # W as reported in paper
      ffm$weight_PA[i] <- ffm$weight_PA[i]^2
    }
  }
}

w_rvi_Pa_w <- brm(logrsd_p| weights(weight_PA) ~ neuro, data= ffm,
                   file = "wp_logrsd_w")
print(w_rvi_Pa_w)
results_wd[5,6] <- extract_param(w_rvi_Pa_w, "b_neuro")

```
# SD

```{r message=TRUE, warning=TRUE}
ffm$sd_NA <- NA
for (i in 1:nrow(ffm)) {
      ffm$sd_NA[i] <- sd(daily_w$panas_n[daily_w$id == ffm$id[i]],
                                   na.rm = T)
    }

ffm$sd_PA <- NA
for (i in 1:nrow(ffm)) {
      ffm$sd_PA[i] <- sd(daily_w$panas_p[daily_w$id == ffm$id[i]],
                                   na.rm = T)
    }

ffm$sd_PA[ffm$sd_PA == 0] <- NA   
ffm$sd_NA[ffm$sd_NA == 0] <- NA   

ffm$logsd_NA <- log(ffm$sd_NA)
ffm$logsd_PA <- log(ffm$sd_PA)

m_sd_na <- brm(logsd_NA ~ neuro, data= ffm,
                file = "wn_logsd")
m_sd_na
results_wd[6,3] <- extract_param(m_sd_na, "b_neuro")

m_sd_pa <- brm(logsd_PA ~ neuro, data= ffm,
               file = "wp_logsd")
m_sd_pa
results_wd[6,6] <- extract_param(m_sd_pa, "b_neuro")
```

# Incremental Validity of SD 

```{r message=TRUE, warning=TRUE}
na_noneurot <- brm(bf(panas_n | cens(Acens) ~  (1|id),
                       sigma ~  (1|id)), data = daily_w,
                       iter = 7000, warmup = 2000,chains = 4,
                      control = list(adapt_delta = .99), init = 0.1,
                   file = "na_noneurot12")

print(na_noneurot)

rans <- coef(na_noneurot, summary = T)


rans_i <- as.data.frame(rans$id[,,"Intercept"]) %>% tibble::rownames_to_column("id")
rans_s <- as.data.frame(rans$id[,,"sigma_Intercept"]) %>% tibble::rownames_to_column("id")
nrow(rans_s)
nrow(rans_i)

dat <- merge(rans_s, rans_i, all = T, by= "id")
dat <- merge(dat, daily_w, all = T, by= "id")
names(dat)[2] <- "Est.SD"
names(dat)[6] <- "Est.M"

fit1 <- lm(neuro ~ Est.SD + Est.M , data=dat)
summary(fit1)

fit1.2 <- lm(neuro ~  Est.M , data=dat)
summary(fit1.2)

aov <- anova(fit1.2, fit1)
aov

summary(fit1)$r.squared-summary(fit1.2)$r.squared

results_SDin <- data.frame(matrix(nrow = 1, ncol = 9))
names(results_SDin) <- c("Dataset","b_SD","Err.SD","p(b_SD)","b_M","Err.M","p(b_M)","ΔR²", "p")

results_SDin$Dataset <- "12"

results_SDin$`ΔR²` <- summary(fit1)$r.squared-summary(fit1.2)$r.squared
results_SDin$`p` <- aov$`Pr(>F)`[2]
results_SDin$Err.SD <- summary(fit1)$coefficients[2,2]
results_SDin$b_SD <- fit1$coefficients[2]

results_SDin$`p(b_SD)` <- summary(fit1)$coefficients[2,4]
results_SDin$b_M <- fit1$coefficients[3]
results_SDin$`p(b_M)` <- summary(fit1)$coefficients[3,4]
results_SDin$Err.M <- summary(fit1)$coefficients[3,2]

```
