---
title: 
author: 
params:
  file: 
output:
  html_document: 
    toc: yes
    number_sections: yes
editor_options: 
  chunk_output_type: console
---

# Data Preparation

```{r,silent=2}
dataset <- read.csv(file = params$file, header = T, sep = ",")
#run parallel cores 
options(mc.cores = 8, brms.backend = "cmdstanr", brms.file_refit = "on_change")
#install.packages("loo")
#remotes::install_github("stan-dev/loo")
library(remotes)
library(loo)
library(psych)
library(relativeVariability)
library(brms)
library(cmdstanr)
library(data.table)
library(ggplot2)
library(dplyr)
library(haven)
#library(rstanarm)
library(knitr)
library(rstan)
library(shinystan)
```


## Rescale Data

```{r}
dataset$negemo_full_m <- (dataset$negemo_full_m -1)*(4/6)+1
dataset$posemo_full_m <- (dataset$posemo_full_m -1)*(4/6)+1

dataset$neuro_t <- (dataset$neuro_t -1)*(4/6)+1

hist(dataset$negemo_full_m)
```

## Censoring Data

```{r}
range(dataset$negemo_full_m, na.rm = T)
range(dataset$posemo_full_m, na.rm = T)
sd(dataset$negemo_full_m, na.rm = T)
mean(dataset$negemo_full_m, na.rm = T)

sd(dataset$posemo_full_m, na.rm = T)
mean(dataset$posemo_full_m, na.rm = T)

sd(dataset$neuro_t, na.rm = T)
mean(dataset$neuro_t, na.rm = T)

qplot(dataset$negemo_full_, binwidth = .1)
qplot(dataset$posemo_full_, binwidth = .1)


dataset$Acens <- case_when(dataset$negemo_full_m == 1 ~ "left",
                         dataset$negemo_full_m == 5 ~ "right",
                         TRUE ~ "none")
table(dataset$Acens)

dataset$Acens_p <- case_when(dataset$posemo_full_m == 1 ~ "left",
                         dataset$posemo_full_m == 5 ~ "right",
                         TRUE ~ "none")
table(dataset$Acens_p)
```

# BCLSM Negative Emotion

```{r message=TRUE, warning=TRUE, silent=2}

Kn_model_neuro3 <- brm(bf(negemo_full_m | cens(Acens) ~ neuro_t + (1|person_id),
                       sigma ~ neuro_t+ (1|person_id)), data = dataset,
                       iter = 7000, warmup = 2000,  chains = 4,
                       control = list(adapt_delta = .99), init = 0.1,
                       file = paste("models/", params$file, "Kn_model_neuro3"))
print(Kn_model_neuro3)
plot(Kn_model_neuro3)
pp_check(Kn_model_neuro3)

prior_summary(Kn_model_neuro3)

```

## Model comparison 
### scale vs. no scale parameter

```{r, silent=2}
Kn_model_neuro2 <- brm(negemo_full_m | cens(Acens) ~ neuro_t + (1|person_id), data = dataset,
                    iter = 6000, warmup = 2000,  chains = 4,
                    control = list(adapt_delta = .98), inits = 0.1 ,
                    file = paste("models/", params$file, "Kn_model_neuro2"))

print(Kn_model_neuro2)


modelA <- Kn_model_neuro2
modelB <- Kn_model_neuro3

modelA <- add_criterion(modelA, "loo")
modelB <- add_criterion(modelB, "loo")

loo <- loo_compare(modelA,modelB, criterion = "loo")

loo <- as.data.frame(loo)

loo$Dataset <- params$file
loo <- tibble::rownames_to_column(loo, "model")
library("writexl")
write_xlsx(loo,paste0("loo", params$file, ".xlsx"))

kable(loo)
```

### censoring vs. no censoring 

```{r, silent=2}
Kn_model_neuro4 <- brm(bf(negemo_full_m  ~ neuro_t + (1|person_id),
                       sigma ~ neuro_t+ (1|person_id)), data = dataset,
                       iter = 7000, warmup = 2000,  chains = 4,
                       control = list(adapt_delta = .9999), init = 0,
                       file = paste("models/", params$file, "Kn_model_neuro4"))
print(Kn_model_neuro4)
```


```{r}
extract_param <- function(model, parameter) {
  ci <- posterior_summary(model, variable = parameter)
  est <- sprintf("%.2f %.2f [%.2f;%.2f]", ci[,"Estimate"],ci[,"Est.Error"], ci[,"Q2.5"], ci[,"Q97.5"])
  est
}

results_Cens <- data.frame(matrix(nrow = 2, 
                             ncol = 6+1)) 
names(results_Cens) <- c("model", "negemo_b_neuro", "negemo_b_neuro_sigma", "negemo_sigma",
                    "posemo_b_neuro", "posemo_b_neuro_sigma", "posemo_sigma"
                    )

results_Cens$model <- c("modelCensoring", "modelnoCensoring")

#NA

results_Cens[1, "negemo_b_neuro"] <- extract_param(Kn_model_neuro3, "b_neuro_t")
results_Cens[1, "negemo_b_neuro_sigma"] <- extract_param(Kn_model_neuro3, "b_sigma_neuro_t")
results_Cens[1, "negemo_sigma"] <- extract_param(Kn_model_neuro3, "b_sigma_Intercept")

results_Cens[2, "negemo_b_neuro"] <- extract_param(Kn_model_neuro4, "b_neuro_t")
results_Cens[2, "negemo_b_neuro_sigma"] <- extract_param(Kn_model_neuro4, "b_sigma_neuro_t")
results_Cens[2, "negemo_sigma"] <- extract_param(Kn_model_neuro4, "b_sigma_Intercept")
```

### BCLSM vs. model C (two-part model)

```{r}
dataset <- dataset %>% left_join(dataset %>% distinct(person_id, neuro_t) %>% mutate(neuro_Q =Hmisc::cut2(neuro_t, g = 4)), by = c("person_id", "neuro_t"))


Kn_model_neuro_jinxed <- brm(bf(negemo_full_m | cens(Acens) ~ neuro_t + (1|gr(person_id, by = neuro_Q)),
  sigma ~ neuro_t + (1|person_id)), data = dataset,
  iter = 5000, warmup = 2000,  chains = 4,
  control = list(adapt_delta = .99), init = 0.1,
  file = paste("models/", params$file, "Kn_model_neuro_jinxed"))


print(Kn_model_neuro_jinxed)
```

```{r}
modelB <- Kn_model_neuro3
modelC <- Kn_model_neuro_jinxed

modelB <- add_criterion(modelB, "loo")
modelC <- add_criterion(modelC, "loo")

loo_c <- loo_compare(modelB,modelC, criterion = "loo")

loo_c <- as.data.frame(loo_c)

loo_c$Dataset <- params$file
loo_c <- tibble::rownames_to_column(loo_c, "model")

library("writexl")
write_xlsx(loo_c,paste0("loo_c", params$file, ".xlsx"))

kable(loo_c)
```

## control for gender 

```{r message=TRUE, warning=TRUE, silent=2}
dataset$gender <- as.factor(dataset$gender)

Kn_model_sex <- brm(bf(negemo_full_m | cens(Acens) ~ neuro_t + gender + (1|person_id),
                       sigma ~ neuro_t + gender), data = dataset,
                       iter = 9000, warmup = 2000, chains = 8,
                       control = list(adapt_delta = .99), inits = 0.1,
                    file = paste("models/", params$file, "Kn_model_sex"))
print(Kn_model_sex)
pp_check(Kn_model_sex)

plot(Kn_model_sex)

```

# BCLSM Positive Emotion

```{r message=TRUE, warning=TRUE, silent=2}
Kp_model_neuro3 <- brm(bf(posemo_full_m | cens(Acens_p) ~ neuro_t + (1|person_id),
                       sigma ~ neuro_t + (1|person_id)), data = dataset,
                       chains = 4,
                       control = list(adapt_delta = .95), inits = 0.1,
                       iter = 7000, warmup = 2000,
                    file = paste("models/", params$file, "Kp_model_neuro3"))
print(Kp_model_neuro3)
pp_check(Kp_model_neuro3)


plot(Kp_model_neuro3)
prior_summary(Kp_model_neuro3)

```

## Model comparison 
### scale vs. no scale parameter

```{r, silent=2}
Kp_model_neuro2 <- brm(posemo_full_m | cens(Acens_p) ~ neuro_t + (1|person_id), data = dataset,
                    iter = 7000, warmup = 2000, chains = 4,
                   control = list(adapt_delta = .95), inits = 0.1,
                    file = paste("models/", params$file, "Kp_model_neuro2"))
print(Kp_model_neuro2)

modelAp <- Kp_model_neuro2
modelBp <- Kp_model_neuro3


modelAp <- add_criterion(modelAp, "loo")
modelBp <- add_criterion(modelBp, "loo")

looP <- loo_compare(modelAp,modelBp, criterion = "loo")

looP <- as.data.frame(looP)

looP$Dataset <- params$file
looP <- tibble::rownames_to_column(looP, "model")
library("writexl")
write_xlsx(looP,paste0("looP", params$file, ".xlsx"))

kable(looP)
```

### censoring vs. no censoring 

```{r, silent=2}
Kp_model_neuro4 <- brm(bf(posemo_full_m ~ neuro_t + (1|person_id),
                       sigma ~ neuro_t + (1|person_id)), data = dataset,
                       chains = 4,
                       control = list(adapt_delta = .9999), inits = 0,
                       iter = 7000, warmup = 2000,
                    file = paste("models/", params$file, "Kp_model_neuro4"))
print(Kp_model_neuro4)
```


```{r, silent=2}
#pa

results_Cens[1, "posemo_b_neuro"] <- extract_param(Kp_model_neuro3, "b_neuro_t")
results_Cens[1, "posemo_b_neuro_sigma"] <- extract_param(Kp_model_neuro3, "b_sigma_neuro_t")
results_Cens[1, "posemo_sigma"] <- extract_param(Kp_model_neuro3, "b_sigma_Intercept")


results_Cens[2, "posemo_b_neuro"] <- extract_param(Kp_model_neuro4, "b_neuro_t")
results_Cens[2, "posemo_b_neuro_sigma"] <- extract_param(Kp_model_neuro4, "b_sigma_neuro_t")
results_Cens[2, "posemo_sigma"] <- extract_param(Kp_model_neuro4, "b_sigma_Intercept")

```

### BCLSM vs. model C (two-part model)

```{r}
Kp_model_neuro_jinxed <- brm(bf(posemo_full_m | cens(Acens) ~ neuro_t + (1|gr(person_id, by = neuro_Q)),
     sigma ~ neuro_t + (1|person_id)), data = dataset,
  iter = 5000, warmup = 2000,  chains = 4,
  control = list(adapt_delta = .99), init = 0.1,
  file = paste("models/", params$file, "Kp_model_neuro_jinxed"))


print(Kp_model_neuro_jinxed)
```

```{r}
modelB <- Kp_model_neuro3
modelC <- Kp_model_neuro_jinxed

modelB <- add_criterion(modelB, "loo")
modelC <- add_criterion(modelC, "loo")

loo_cP <- loo_compare(modelB,modelC, criterion = "loo")

loo_cP <- as.data.frame(loo_cP)

loo_cP$Dataset <- params$file
#loo_cP <- tibble::rownames_to_column(loo_c, "model")
library("writexl")
write_xlsx(loo_cP,paste0("loo_cP", params$file, ".xlsx"))

kable(loo_cP)
```


```{r}
extract_param <- function(model, parameter) {
  ci <- posterior_summary(model, variable = parameter)
  est <- sprintf("%.2f %.2f [%.2f;%.2f]", ci[,"Estimate"],ci[,"Est.Error"], ci[,"Q2.5"], ci[,"Q97.5"])
  est
}

results_K <- data.frame(matrix(nrow = 7, 
                             ncol = 8+1)) 
names(results_K) <- c("model", "negemo_b_neuro", "negemo_b_neuro_sigma", "negemo_sigma", "b_neg_sigma_sex",
                    "posemo_b_neuro", "posemo_b_neuro_sigma", "posemo_sigma", "b_pos_sigma_sex"
                    )

results_K$model <- c("model1", "model2", "model3",
                  "RSD", "RSD_weight", "SD", "gender")

#NA

results_K[2, "negemo_b_neuro"] <- extract_param(Kn_model_neuro2, "b_neuro_t")
results_K[2, "negemo_sigma"] <- extract_param(Kn_model_neuro2, "sigma")

results_K[3, "negemo_b_neuro"] <- extract_param(Kn_model_neuro3, "b_neuro_t")
results_K[3, "negemo_b_neuro_sigma"] <- extract_param(Kn_model_neuro3, "b_sigma_neuro_t")
results_K[3, "negemo_sigma"] <- extract_param(Kn_model_neuro3, "b_sigma_Intercept")
```


```{r}
#gender 

results_K[7, "negemo_b_neuro"] <- extract_param(Kn_model_sex, "b_neuro_t")
results_K[7, "negemo_b_neuro_sigma"] <- extract_param(Kn_model_sex, "b_sigma_neuro_t")
results_K[7, "negemo_sigma"] <- extract_param(Kn_model_sex, "b_sigma_Intercept")
results_K[7, "b_neg_sigma_sex"] <- extract_param(Kn_model_sex, "b_sigma_gender1")
```


```{r}
#pa
results_K[2, "posemo_b_neuro"] <- extract_param(Kp_model_neuro2, "b_neuro_t")
results_K[2, "posemo_sigma"] <- extract_param(Kp_model_neuro2, "sigma")

results_K[3, "posemo_b_neuro"] <- extract_param(Kp_model_neuro3, "b_neuro_t")
results_K[3, "posemo_b_neuro_sigma"] <- extract_param(Kp_model_neuro3, "b_sigma_neuro_t")
results_K[3, "posemo_sigma"] <- extract_param(Kp_model_neuro3, "b_sigma_Intercept")


```

# RVI (Relative Variability Index)

```{r silent=2}
data_w <- unique(dataset[,2:5])
```

## Unweighted RVI

```{r, silent=2, warning=FALSE}
data_w$RSD_NA <- NA
for (i in 1:nrow(data_w)) {
      data_w$RSD_NA[i] <- relativeSD(dataset$negemo_full_m[dataset$person_id == data_w$person_id[i]],
                                     1, 5)
    }

range(data_w$RSD_NA, na.rm = T)
mean(data_w$RSD_NA, na.rm = T)
sd(data_w$RSD_NA, na.rm = T)

data_w$logrsd_n <- log(data_w$RSD_NA)

#plot(data_w$logrsd_n)

m_rvi_na <- brm(logrsd_n ~ neuro_t, data= data_w,
                file = paste("models/", params$file, "Kn_model_logrsd_uw"))
print(m_rvi_na)
results_K[4,3] <- extract_param(m_rvi_na, "b_neuro_t")



data_w$RSD_PA <- NA
for (i in 1:nrow(data_w)) {
      data_w$RSD_PA[i] <- relativeSD(dataset$posemo_full_m[dataset$person_id == data_w$person_id[i]],
                                     1, 5)
}

range(data_w$RSD_PA)

data_w$logrsd_p <- log(data_w$RSD_PA)


m_rvi_pa <- brm(logrsd_p ~ neuro_t, data= data_w,
                 file = paste("models/", params$file, "Kp_model_logrsd_uw"))
print(m_rvi_pa)

results_K[4,6] <- extract_param(m_rvi_pa, "b_neuro_t")

```

## Weighted RVI

```{r silent=2}
data_w$mean_NA <- NA
for (i in 1:nrow(data_w)) {
      data_w$mean_NA[i] <- mean(dataset$negemo_full_m[dataset$person_id == data_w$person_id[i]],
                                   na.rm = T)
    }

mean(data_w$mean_NA)
sd(data_w$mean_NA)


data_w$mean_PA <- NA
for (i in 1:nrow(data_w)) {
      data_w$mean_PA[i] <- mean(dataset$posemo_full_m[dataset$person_id == data_w$person_id[i]],
                                   na.rm = T)
}

mean(data_w$mean_PA)
sd(data_w$mean_PA)
```


```{r silent=2}

data_w$weight_NA <- NA
for (i in 1:nrow(data_w)) {
    if (!is.na(data_w$mean_NA[i])) {
      data_w$weight_NA[i] <- maximumSD(data_w$mean_NA[i], # Mittelwert
                                       1,  # Minimum
                                       5,  # Maximum
                                       sum(!is.na(dataset$negemo_full_m[dataset$person_id == data_w$person_id[i]])) 
      ) 
      # W as reported in paper
      data_w$weight_NA[i] <- data_w$weight_NA[i]^2
    }
  }

mean(data_w$weight_NA)
sd(data_w$weight_NA)
range(data_w$weight_NA)

m_rvi_na_w <- brm(logrsd_n| weights(weight_NA) ~ neuro_t, data= data_w,
                    file = paste("models/", params$file, "Kn_model_logrsd"))
print(m_rvi_na_w)
results_K[5,3] <- extract_param(m_rvi_na_w, "b_neuro_t")



data_w$weight_PA <- NA
for (i in 1:nrow(data_w)) {
    if (!is.na(data_w$mean_PA[i])) {
      data_w$weight_PA[i] <- maximumSD(data_w$mean_PA[i], # Mittelwert
                                       1,  # Minimum
                                       5,  # Maximum
                                       sum(!is.na(dataset$posemo_full_m[dataset$person_id == data_w$person_id[i]])) 
      ) 
      # W as reported in paper
      data_w$weight_PA[i] <- data_w$weight_PA[i]^2
    }
  }

m_rvi_pa_w <- brm(logrsd_p| weights(weight_PA) ~ neuro_t, data= data_w,
                    file = paste("models/", params$file, "Kp_model_logrsd"))
print(m_rvi_pa_w)
results_K[5,6] <- extract_param(m_rvi_pa_w, "b_neuro_t")

```

# SD

```{r silent=2}
data_w$sd_NA <- NA
for (i in 1:nrow(data_w)) {
      data_w$sd_NA[i] <- sd(dataset$negemo_full_m[dataset$person_id == data_w$person_id[i]],
                                   na.rm = T)
    }

data_w$sd_PA <- NA
for (i in 1:nrow(data_w)) {
      data_w$sd_PA[i] <- sd(dataset$posemo_full_m[dataset$person_id == data_w$person_id[i]],
                                   na.rm = T)
    }

mean(data_w$sd_NA)
mean(data_w$sd_PA)
data_w$sd_PA[data_w$sd_PA == 0] <- NA   
data_w$sd_NA[data_w$sd_NA == 0] <- NA   


data_w$logsd_NA <- log(data_w$sd_NA)
data_w$logsd_PA <- log(data_w$sd_PA)
```


```{r silent=2}
m_sd_na <- brm(logsd_NA ~ neuro_t, data= data_w,
                    file = paste("models/", params$file, "Kn_model_logsd"))
m_sd_na

results_K[6,3] <- extract_param(m_sd_na, "b_neuro_t")

m_sd_pa <- brm(logsd_PA ~ neuro_t, data= data_w,
                    file = paste("models/", params$file, "Kp_model_logsd"))
m_sd_pa
results_K[6,6] <- extract_param(m_sd_pa, "b_neuro_t")
```


```{r message=TRUE, warning=TRUE}
library("writexl")

write_xlsx(results_K,paste0("", params$file, ".xlsx"))
         
```


# Incremental Validity of SD 

```{r silent=2}
na_noneurot <- brm(bf(negemo_full_m | cens(Acens) ~  (1|person_id),
                       sigma ~ (1|person_id)), data = dataset,
                       iter = 7000, warmup = 2000,chains = 4,
                      control = list(adapt_delta = .99), init = 0.1,
                   file = "na_noneurot")

print(na_noneurot)

rans <- coef(na_noneurot, summary = T)


rans_i <- as.data.frame(rans$person_id[,,"Intercept"]) %>% tibble::rownames_to_column("person_id")
rans_s <- as.data.frame(rans$person_id[,,"sigma_Intercept"]) %>% tibble::rownames_to_column("person_id")
nrow(rans_s)
nrow(rans_i)
nrow(data_w)
dat <- merge(rans_s, rans_i, all = T, by= "person_id")
dat <- merge(dat, data_w, all = T, by= "person_id")

names(dat)[2] <- "Est.SD"
names(dat)[6] <- "Est.M"

fit1 <- lm(neuro_t ~ Est.SD + Est.M , data=dat)
summary(fit1)

fit1.2 <- lm(neuro_t ~  Est.M , data=dat)
summary(fit1.2)

aov <- anova(fit1.2, fit1)
aov

summary(fit1)$r.squared-summary(fit1.2)$r.squared

results_SDin <- data.frame(matrix(nrow = 1, ncol = 9))
names(results_SDin) <- c("Dataset","b_SD","Err.SD","p(b_SD)","b_M","Err.M","p(b_M)","ΔR²", "p")

results_SDin$Dataset <- params$file

results_SDin$`ΔR²` <- summary(fit1)$r.squared-summary(fit1.2)$r.squared
results_SDin$`p` <- aov$`Pr(>F)`[2]
results_SDin$Err.SD <- summary(fit1)$coefficients[2,2]
results_SDin$b_SD <- fit1$coefficients[2]

results_SDin$`p(b_SD)` <- summary(fit1)$coefficients[2,4]
results_SDin$b_M <- fit1$coefficients[3]
results_SDin$`p(b_M)` <- summary(fit1)$coefficients[3,4]
results_SDin$Err.M <- summary(fit1)$coefficients[3,2]

  
library("writexl")
write_xlsx(results_SDin,paste0("SD", params$file, ".xlsx"))

```

