---
title: "Main Simulation"
output:
  html_document: 
    toc: yes
    number_sections: yes
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidybayes)
library(psych)
library(distributional)
library(ggdist )
#install.packages("~/rstudio01/Neu/relativeVariability_1.0.tar.gz", repos = NULL, type = "source")


library(relativeVariability)
library(brms)
library(cmdstanr)
library(knitr)
library(rstan)
library(shinystan)

#run parallel cores 
options(mc.cores =8, brms.backend = "cmdstanr", brms.file_refit = "on_change")
check_cmdstan_toolchain()

set_cmdstan_path()

cmdstan_path()
```

# Simulate Data

Create a sample with neuroticism scores (normal distributed)

```{r}
set.seed(040519)

n <- 200
days_per_person <- 30
n_days <- n*days_per_person

people <- tibble(
  id = 1:n,
  neurot = rnorm(n), 
  latentaffect = rnorm(n), 
  latentaffectsd = rnorm(n), 
  
)
sd(people$neurot)

```
This is how we simulate measurement.
(measure: censored 1-5)

```{r cars}
measure <- function(x) {
  x[x < -2] <- -2
  x[x > 2] <- 2
  round(x,1) +3
}
```

## 3 true models 
model 1: association with the mean (diary1)
model 2: association with variability (diary2)
model 3: both(diary3)

```{r}

diary1 <-  people %>% full_join(
   tibble(
     id = rep(1:n, each = days_per_person),
   ), by = 'id') %>%
   mutate(
     Aff1 =  -1.4 + 0.5* neurot + 0.3* latentaffect +
        rnorm(n_days, mean =0 , sd = exp(-1.1 + 0 * neurot + 0.3* latentaffectsd))
   )

qplot(diary1$neurot, diary1$Aff1, alpha = I(0.1)) + geom_hline(yintercept = -2, linetype = "dashed")
qplot(diary1$Aff1)
qplot(measure(diary1$Aff1), binwidth = .1)
sd(diary1$Aff1[6001:9000])

diary1  %>% group_by(id, neurot)  %>% 
  summarise(Aff1 = mean(Aff1)) %>% ungroup() %>% summarise(cor(Aff1, neurot))


sd(diary1$neurot)
sd(diary1$Aff1)
hist(diary1$Aff1)
qplot(diary1$neurot, diary1$Aff1)


diary2 <-  people %>% full_join(
   tibble(
     id = rep(1:n, each = days_per_person),
   ), by = 'id') %>%
   mutate(
     Aff2 =  -1.4 + 0 * neurot + 0.3* latentaffect +
        rnorm(n_days, mean = 0, sd = exp(-1.1 +0.15 * neurot + 0.3*latentaffectsd))
   )

sd(diary2$Aff2)
qplot(diary2$Aff2)
qplot(diary2$neurot, diary2$Aff2, alpha = I(0.1)) + geom_hline(yintercept = -2, linetype = "dashed")
qplot(measure(diary2$Aff2), binwidth = .1)



diary3 <-  people %>% full_join(
   tibble(
     id = rep(1:n, each = days_per_person),
   ), by = 'id') %>%
   mutate(
     Aff3 =  -1.4 + 0.5 * neurot + 0.3*latentaffect +
        rnorm(n_days, mean = 0, sd = exp(-1.1 + 0.15 * neurot + 0.3* latentaffectsd))
   )

sd(diary3$neurot)
sd(diary3$Aff3)
qplot(diary3$neurot, diary3$Aff3, alpha = I(0.1)) + geom_hline(yintercept = -2, linetype = "dashed")
qplot(measure(diary3$Aff3), binwidth = .1)
sd(measure(diary3$Aff3), na.rm=T)
qplot(diary3$Aff3, binwidth = .1)
```


Add measured Affect to all three Simulations

```{r}
diary1 <- diary1 %>%  
  mutate(
    Affect_m =  measure(Aff1)                          
  )
sd(diary1$Affect_m)
round(cor(diary1 %>% select(Aff1, Affect_m)),2)   
qplot(diary1$Affect_m, binwidth=.1)


diary2 <- diary2 %>%  
  mutate(
    Affect_m =  measure(Aff2 )                          
  )

sd(diary2$Affect_m)
round(cor(diary2 %>% select(Aff2, Affect_m)),2)   
qplot(diary2$Affect_m, binwidth=.1)

diary3 <- diary3 %>%  
  mutate(
    Affect_m =  measure(Aff3)                          
  )
sd(diary3$Affect_m)
#round(cor(diary3 %>% select(Aff3, Affect_m)),2)   
qplot(diary3$Affect_m, binwidth=.1)
```


```{r}
diary1$Acens <- case_when(diary1$Affect_m == 1 ~ "left",
                         diary1$Affect_m == 5 ~ "right",
                         TRUE ~ "none")
table(diary1$Acens)

```

```{r}
diary2$Acens <- case_when(diary2$Affect_m == 1 ~ "left",
                         diary2$Affect_m == 5 ~ "right",
                         TRUE ~ "none")
table(diary2$Acens)


diary3$Acens <- case_when(diary3$Affect_m == 1 ~ "left",
                         diary3$Affect_m == 5 ~ "right",
                         TRUE ~ "none")
table(diary3$Acens)


```

Add measured neuroticism to all three Simulations 

```{r}

measure_n <- function(x) {
  # expects that x is N(0,1)
  x <- x 
   
  round(x,1) 
}

diary1 <- diary1 %>%  
  mutate(
    neurot_m =  measure_n(neurot)                          
  )
sd(diary1$neurot_m)
#round(cor(diary1 %>% select(neurot, neurot_m)),2)   
qplot(diary1$neurot_m, binwidth=.1)


diary2 <- diary2 %>%  
  mutate(
    neurot_m =  measure_n(neurot)                          
  )
sd(diary2$neurot_m)
#round(cor(diary2 %>% select(neurot, neurot_m)),2)   
#qplot(diary2$neurot_m, binwidth=.1)


diary3 <- diary3 %>%  
  mutate(
    neurot_m =  measure_n(neurot)                          
  )
sd(diary3$neurot_m)
#round(cor(diary3 %>% select(neurot, neurot_m)),2)   
#qplot(diary3$neurot_m, binwidth=.1)


```

# Estimated models

model 1: naiv: only associations with the mean, normal distribution assumption
model 2: associations with the mean, censored
model 3: association with mean and variability, censored

## Simulation 1 (effect on mean) BCLSM

```{r message=TRUE, warning=TRUE}
w1model_neuro3 <- brm(bf(Affect_m | cens(Acens) ~ neurot_m + (1|id),
                       sigma ~ neurot_m + (1|id)), data = diary1,
                    iter = 6000, warmup = 2000, init = 0.1,
                    file = "w1model_neuro3")


print(w1model_neuro3)
plot(w1model_neuro3)
```



## Simulation 2 (effect on  SD) BCLSM


```{r message=TRUE, warning=TRUE}
w2model_neuro3 <- brm(bf(Affect_m | cens(Acens) ~ neurot_m + (1|id),
                    sigma ~ neurot_m + (1|id)), data = diary2,
                    control = list(adapt_delta = .99),chains = 8,
                    iter = 6000, warmup = 2000, init = 0.1,
                   file = "w2model_neuro3")
print(w2model_neuro3)
plot(w2model_neuro3)
```

## Simulation 3 (effects on both) BCLSM


```{r message=TRUE, warning=TRUE}
w3model_neuro3 <- brm(bf(Affect_m| cens(Acens)  ~ neurot_m + (1|id),
                       sigma ~ neurot_m + (1|id)), data = diary3,
                      iter = 7000, warmup = 2000,chains = 8,
                    control = list(adapt_delta = .99), inits = 0.1 ,        #options = list(adapt_delta = 0.99)
                   file = "w3model_neuro3")
print(w3model_neuro3)
plot(w3model_neuro3)
```


```{r}
extract_param2 <- function(model, parameter) {
  ci <- posterior_summary(model, variable = parameter)
  est <- sprintf("%.4f %.4f %.4f", ci[,"Estimate"], ci[,"Q2.5"], ci[,"Q97.5"])
  est
}

results_sim <- data.frame(matrix(nrow = 8, 
                             ncol = 9+1))  
names(results_sim) <- c("model", "w1_b_neuro", "w1_b_neuro_sigma", "w1_sigma",
                    "w2_b_neuro", "w2_b_neuro_sigma", "w2_sigma",
                    "w3_b_neuro", "w3_b_neuro_sigma", "w3_sigma"
                    )

results_sim$model <- c("model1", "model2", "BCLSM",
                  "RVI", "RVI_weight", "SD", "SD*", "BLSM")


```


```{r}
results_sim[3, "w1_b_neuro"] <- extract_param2(w1model_neuro3, "b_neurot_m")
results_sim[3, "w1_b_neuro_sigma"] <- extract_param2(w1model_neuro3, "b_sigma_neurot_m")
results_sim[3, "w1_sigma"] <- extract_param2(w1model_neuro3, "b_sigma_Intercept")
```


```{r}
results_sim[3, "w2_b_neuro"] <- extract_param2(w2model_neuro3, "b_neurot_m")
results_sim[3, "w2_b_neuro_sigma"] <- extract_param2(w2model_neuro3, "b_sigma_neurot_m")
results_sim[3, "w2_sigma"] <- extract_param2(w2model_neuro3, "b_sigma_Intercept")


```

```{r}
results_sim[3, "w3_b_neuro"] <- extract_param2(w3model_neuro3, "b_neurot_m")
results_sim[3, "w3_b_neuro_sigma"] <- extract_param2(w3model_neuro3, "b_sigma_neurot_m")
results_sim[3, "w3_sigma"] <- extract_param2(w3model_neuro3, "b_sigma_Intercept")
```

# RVI (Relative-Variability-Index) 
## Unweighted RVI for all three Simulations

```{r}
# Neurot Measure 
people <- people %>%  
  mutate(
    neurot =  measure_n(neurot)                          
  )

id <- unique(diary1$id)
id <- as.data.frame(id)

people$RSD_d1 <- NA
for (i in 1:nrow(id)) {
  if (id$id[i] %in% diary1$id) {
      people$RSD_d1[i] <- relativeSD(diary1$Affect_m[diary1$id == id$id[i]],
                                         1, 5)
    }
  } 


people$logrsd_d1 <- log(people$RSD_d1)

m_rsd_d1 <- brm(logrsd_d1 ~ neurot, data= people,
                file="simneg1_logrsd_uw")
print(m_rsd_d1, digits=4)



results_sim[4,3] <- extract_param2(m_rsd_d1, "b_neurot")
 


people$RSD_d2 <- NA
for (i in 1:nrow(id)) {
  if (id$id[i] %in% diary2$id) {
      people$RSD_d2[i] <- relativeSD(diary2$Affect_m[diary2$id == id$id[i]],
                                         1, 5)
    }
  } 

people$logrsd_d2 <- log(people$RSD_d2)


m_rsd_d2 <- brm( logrsd_d2~ neurot, data= people,
                 file="simneg2_logrsd_uw")
m_rsd_d2
results_sim[4,6] <- extract_param2(m_rsd_d2, "b_neurot")


people$RSD_d3 <- NA
for (i in 1:nrow(id)) {
  if (id$id[i] %in% diary3$id) {
      people$RSD_d3[i] <- relativeSD(diary3$Affect_m[diary3$id == id$id[i]],
                                         1, 5)
    }
  } 

people$logrsd_d3 <- log(people$RSD_d3)



m_rsd_d3 <- brm(logrsd_d3 ~ neurot, data= people,
                file="simneg3_logrsd_uw")
m_rsd_d3
results_sim[4,9] <- extract_param2(m_rsd_d3, "b_neurot")


```

## weighted RVI for all three Simulations 
 
```{r}
people$mean_Aff_d1 <- NA
for (i in 1:nrow(id)) {
  if (id$id[i] %in% diary1$id) {
      people$mean_Aff_d1[i] <- mean(diary1$Affect_m[diary1$id == id$id[i]],
                                   na.rm = T)
    }
  } 

range(people$mean_Aff_d1)

people$mean_Aff_d2 <- NA
for (i in 1:nrow(id)) {
  if (id$id[i] %in% diary2$id) {
      people$mean_Aff_d2[i] <- mean(diary2$Affect_m[diary2$id == id$id[i]],
                                   na.rm = T)
    }
  } 

range(people$mean_Aff_d2)


people$mean_Aff_d3 <- NA
for (i in 1:nrow(id)) {
  if (id$id[i] %in% diary3$id) {
      people$mean_Aff_d3[i] <- mean(diary3$Affect_m[diary3$id == id$id[i]],
                                   na.rm = T)
    }
  } 

range(people$mean_Aff_d3)

```

```{r}
people$weight_d1 <- NA
for (i in 1:nrow(id)) {
  if (id$id[i] %in% diary1$id) {
      people$weight_d1[i] <- maximumSD(people$mean_Aff_d1[i], 
                                       1,  # Minimum
                                       5,  # Maximum
                                       sum(!is.na(diary1$Affect_m[diary1$id == id$id[i]])) # Anzahl Beobachtungen in var eingeflossen/30
      ) 
      # W as reported in paper
      people$weight_d1[i] <- people$weight_d1[i]^2
    }
}

people$weight_d2 <- NA
for (i in 1:nrow(id)) {
  if (id$id[i] %in% diary2$id) {
      people$weight_d2[i] <- maximumSD(people$mean_Aff_d2[i], 
                                       1,  # Minimum
                                       5,  # Maximum
                                       sum(!is.na(diary2$Affect_m[diary2$id == id$id[i]])) # Anzahl Beobachtungen in var eingeflossen/30
      ) 
      # W as reported in paper
      people$weight_d2[i] <- people$weight_d2[i]^2
    }
}

people$weight_d3 <- NA
for (i in 1:nrow(id)) {
  if (id$id[i] %in% diary3$id) {
      people$weight_d3[i] <- maximumSD(people$mean_Aff_d3[i], 
                                       1,  # Minimum
                                       5,  # Maximum
                                       sum(!is.na(diary3$Affect_m[diary3$id == id$id[i]])) # Anzahl Beobachtungen in var eingeflossen/30
      ) 
      # W as reported in paper
      people$weight_d3[i] <- people$weight_d3[i]^2
    }
}

```


```{r}
m_rsd_d1_w <- brm(logrsd_d1| weights(weight_d1) ~ neurot, data= people,
                  file="simneg1_logrsd_w")
m_rsd_d1_w
results_sim[5,3] <- extract_param2(m_rsd_d1_w, "b_neurot")

m_rsd_d2_w <- brm(logrsd_d2| weights(weight_d2) ~ neurot, data= people,
                  file="simneg2_logrsd_w")
m_rsd_d2_w
results_sim[5,6] <- extract_param2(m_rsd_d2_w, "b_neurot")

m_rsd_d3_w <- brm(logrsd_d3| weights(weight_d3) ~ neurot, data= people,
                  file="simneg3_logrsd_w")
m_rsd_d3_w
results_sim[5,9] <- extract_param2(m_rsd_d3_w, "b_neurot")
```


# SD

```{r}
people$sd_Aff_d1 <- NA
for (i in 1:nrow(id)) {
  if (id$id[i] %in% diary1$id) {
      people$sd_Aff_d1[i] <- sd(diary1$Affect_m[diary1$id == id$id[i]],
                                   na.rm = T)
    }
}

people$sd_Aff_d2 <- NA
for (i in 1:nrow(id)) {
  if (id$id[i] %in% diary2$id) {
      people$sd_Aff_d2[i] <- sd(diary2$Affect_m[diary2$id == id$id[i]],
                                   na.rm = T)
    }
}

people$sd_Aff_d3 <- NA
for (i in 1:nrow(id)) {
  if (id$id[i] %in% diary3$id) {
      people$sd_Aff_d3[i] <- sd(diary3$Affect_m[diary3$id == id$id[i]],
                                   na.rm = T)
    }
}

people$sd_Aff_d1[people$sd_Aff_d1 == 0] <- NA   
people$sd_Aff_d2[people$sd_Aff_d2 == 0] <- NA   
people$sd_Aff_d3[people$sd_Aff_d3 == 0] <- NA   

people$logsd_d1 <- log(people$sd_Aff_d1)
people$logsd_d2 <- log(people$sd_Aff_d2)
people$logsd_d3 <- log(people$sd_Aff_d3)




mean(people$sd_Aff_d1)  
mean(people$sd_Aff_d2)  
mean(people$sd_Aff_d3, na.rm = T)  
```

## Regression with SD

```{r}

m_sd_d1 <- brm(logsd_d1 ~ neurot, data= people,
               file="simneg1_logsd")
m_sd_d1
results_sim[6,3] <- extract_param2(m_sd_d1, "b_neurot")


m_sd_d2 <- brm(logsd_d2 ~ neurot, data= people,
               file="simneg2_logsd")
m_sd_d2
results_sim[6,6] <- extract_param2(m_sd_d2, "b_neurot")

m_sd_d3 <- brm(logsd_d3 ~ neurot, data= people,
               file="simneg3_logsd")
m_sd_d3
results_sim[6,9] <- extract_param2(m_sd_d3, "b_neurot")

```

## Regression with SD + controlling for mean values of negative Emotion 

```{r}

m_sd_d1c <- brm(logsd_d1 ~ neurot + mean_Aff_d1, data= people,
                file="simneg1_logsd_m")
m_sd_d1c
results_sim[7,3] <- extract_param2(m_sd_d1c, "b_neurot")


m_sd_d2c <- brm(logsd_d2 ~ neurot + mean_Aff_d2, data= people,
                file="simneg2_logsd_m")
m_sd_d2c
results_sim[7,6] <- extract_param2(m_sd_d2c, "b_neurot")

m_sd_d3c <- brm(logsd_d3 ~ neurot + mean_Aff_d3, data= people,
                 file="simneg3_logsd_m")
m_sd_d3c
results_sim[7,9] <- extract_param2(m_sd_d3c, "b_neurot")

```

# BLSM without Censoring 

## Simulation 1 BLSM 

```{r message=TRUE, warning=TRUE}

people_1 <- people[order(people$mean_Aff_d1),]
people_1e <- people_1[-c(1:10),]
high_1 <- diary1[(diary1$id %in% people_1e$id),]

w1model_neuro4b <- brm(bf(Affect_m  ~ neurot_m + (1|id),
                       sigma ~ neurot_m + (1|id)), data = high_1,
                       control = list(adapt_delta = .99999),chains = 4,
                        iter = 7000, warmup = 2000, init = 0.1,
                    file = "w1model_neuro4b")



print(w1model_neuro4b)
plot(w1model_neuro4b)
```

## Simulation 2 BLSM

```{r message=TRUE, warning=TRUE}
people_2 <- people[order(people$mean_Aff_d2),]
people_2e <- people_2[-c(1:10),]
high_2 <- diary2[(diary2$id %in% people_2e$id),]

w2model_neuro4b <- brm(bf(Affect_m  ~ neurot_m + (1|id),
                    sigma ~ neurot_m + (1|id)), data = high_2,
                    control = list(adapt_delta = .9999),chains = 4,
                    iter = 6000, warmup = 2000, init = 0.1,
                   file = "w2model_neuro4b")
print(w2model_neuro4b)

```

## Simulation 3 BLSM

```{r message=TRUE, warning=TRUE}
people_3 <- people[order(people$mean_Aff_d3),]
people_3e <- people_3[-c(1:10),]
high_3 <- diary3[(diary3$id %in% people_3e$id),]

w3model_neuro4b <- brm(bf(Affect_m  ~ neurot_m + (1|id),
                       sigma ~ neurot_m + (1|id)), data = high_3,
                      iter = 7000, warmup = 2000,chains = 4,
                    control = list(adapt_delta = .9999), inits = 0.1 ,        #options = list(adapt_delta = 0.99)
                   file = "w3model_neuro4b")
print(w3model_neuro4b)
plot(w3model_neuro4b)

```

```{r}
results_sim[8, "w1_b_neuro"] <- extract_param2(w1model_neuro4b, "b_neurot_m")
results_sim[8, "w1_b_neuro_sigma"] <- extract_param2(w1model_neuro4b, "b_sigma_neurot_m")
results_sim[8, "w1_sigma"] <- extract_param2(w1model_neuro4b, "b_sigma_Intercept")

results_sim[8, "w2_b_neuro"] <- extract_param2(w2model_neuro4b, "b_neurot_m")
results_sim[8, "w2_b_neuro_sigma"] <- extract_param2(w2model_neuro4b, "b_sigma_neurot_m")
results_sim[8, "w2_sigma"] <- extract_param2(w2model_neuro4b, "b_sigma_Intercept")

results_sim[8, "w3_b_neuro"] <- extract_param2(w3model_neuro4b, "b_neurot_m")
results_sim[8, "w3_b_neuro_sigma"] <- extract_param2(w3model_neuro4b, "b_sigma_neurot_m")
results_sim[8, "w3_sigma"] <- extract_param2(w3model_neuro4b, "b_sigma_Intercept")
```

