---
title: "MetaAnalysis"
output:
  html_document: 
    toc: yes
    number_sections: yes
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(stringr)
library(metafor)
library(dplyr)
library(tidyverse)
library(readxl)
```

# Aggregate Results

```{r}
#create list with files from Kalokerinos Study
kalok_files = paste0("Dataset ", 1:11, " public.csv.xlsx")

# add Dataset 12  
kalok_files <- append(kalok_files, "results_wd.xlsx" )

#add Dataset 13
kalok_files <-  append(kalok_files, "results_LS.xlsx")

#read data
K_data <- lapply(kalok_files, read_excel)


# adding column with name of dataset
for( i in 1:13){
  
  K_data[[i]]$Dataset <- NA
}

for( i in 1:13){
  
  K_data[[i]]$Dataset <- rep(i, 7)
}

K_data <-  bind_rows(K_data) 

#add author names 

K_data$Dataset[K_data$Dataset == 1] <- "Van Ryckeghem et al."
K_data$Dataset[K_data$Dataset == 2] <- "Dejonckheere et al."
K_data$Dataset[K_data$Dataset == 3] <- "Kalokerinos et al."
K_data$Dataset[K_data$Dataset == 4] <- "Grommisch et al."
K_data$Dataset[K_data$Dataset == 5] <- "Erbas et al."
K_data$Dataset[K_data$Dataset == 6] <- "Brans et al."
K_data$Dataset[K_data$Dataset == 7] <- "Holland et al."
K_data$Dataset[K_data$Dataset == 8] <- "Koval et al."
K_data$Dataset[K_data$Dataset == 9] <- "Koval et al."
K_data$Dataset[K_data$Dataset == 10] <- "Dejonckheere et al."
K_data$Dataset[K_data$Dataset == 11] <- "Kalokerinos et al."
K_data$Dataset[K_data$Dataset == 12] <- "Denissen et al."
K_data$Dataset[K_data$Dataset == 13] <- "Own diary data"


K_data <-  bind_rows(K_data)
```

# Data Preparation

```{r}
### seperate columns in value, est.error and CI

K_data <- K_data %>% 
  tidyr::separate(negemo_b_neuro,                      
                  c("neg_b_neuro", "est.error_n_b_neuro", "KIn_b_neuro"), sep = " ")

K_data <-K_data %>% 
  tidyr::separate(negemo_b_neuro_sigma,                      
                  c("neg_b_neuro_sigma", "est.error_n_b_neuro_sigma", "KIn_b_neuro_sigma"), sep = " ")

K_data <-K_data %>% 
  tidyr::separate(posemo_b_neuro,                      
                  c("pos_b_neuro", "est.error_p_b_neuro", "KIp_b_neuro"), sep = " ")

K_data <-K_data %>% 
  tidyr::separate(posemo_b_neuro_sigma,                      
                  c("pos_b_neuro_sigma", "est.error_p_b_neuro_sigma", "KIp_b_neuro_sigma"), sep = " ")

K_data <-K_data %>% 
  tidyr::separate(b_neg_sigma_sex,                      
                  c("b_neg_sigma_sex", "est.error_b_neg_sigma_sex", "KIb_neg_sigma_sex"), sep = " ")


K_data <-K_data %>% 
  tidyr::separate(b_pos_sigma_sex,                      
                  c("b_pos_sigma_sex", "est.error_b_pos_sigma_sex", "KIb_pos_sigma_sex"), sep = " ")

# save Table 
library("writexl")

write_xlsx(K_data,"~/new_results2.xlsx")

## Filter Dataset for plots 
K_b_sigma <- K_data %>% filter(model== "model3")
K_RSD <- K_data %>% filter(model == "RSD")
K_RSD_w <- K_data %>% filter(model == "RSD_weight")
K_gender <- K_data %>% filter(model == "gender") 
K_SD <- K_data %>% filter(model == "SD") 

```

# Plot Data 

```{r}
apatheme = theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        panel.border = element_blank(),
        text=element_text(family='Arial'),
        legend.title=element_blank(),
        legend.position=c(.7,.8),
        axis.line.x = element_line(color='black'),
        axis.line.y = element_line(color='black'))
```

## BCLSM

### Meta-Analysis b sigma negative

```{r}
# 1. b sigma 
K_b_sigma$est.error_n_b_neuro_sigma <- as.numeric( K_b_sigma$est.error_n_b_neuro_sigma)
K_b_sigma$neg_b_neuro_sigma <- as.numeric( K_b_sigma$neg_b_neuro_sigma)

mod_b_sigma <-  rma(yi= neg_b_neuro_sigma, sei= est.error_n_b_neuro_sigma, data= K_b_sigma )  
summary(mod_b_sigma)
forest(mod_b_sigma, slab =c(paste0(1:13,".", " ", K_b_sigma$Dataset)), 
       mlab = (paste("Random Effects Model Study 1-13 "))) 
par(bg="white")
```

### Meta-Analysis b sigma positive

```{r}
K_b_sigma$est.error_p_b_neuro_sigma <- as.numeric( K_b_sigma$est.error_p_b_neuro_sigma)
K_b_sigma$pos_b_neuro_sigma <- as.numeric( K_b_sigma$pos_b_neuro_sigma)

mod_b_sigma2 <-  rma(yi= pos_b_neuro_sigma, sei= est.error_p_b_neuro_sigma, data= K_b_sigma )  
summary(mod_b_sigma2)

pos_sigma <- forest(mod_b_sigma2, slab =c(paste0(1:13,".", " ", K_b_sigma$Dataset)), 
                    xlim=c(-0.6,0.6), at=seq(-0.2,0.3,by=.1),
                    mlab = (paste("Random Effects Model Study 1-13 "))) 
pos_sigma
```

### Meta-Analysis b mean negative
```{r}
# b mean 

K_b_sigma$est.error_n_b_neuro <- as.numeric( K_b_sigma$est.error_n_b_neuro)
K_b_sigma$neg_b_neuro <- as.numeric( K_b_sigma$neg_b_neuro)

mod_b <-  rma(yi= neg_b_neuro, sei= est.error_n_b_neuro, data= K_b_sigma )  
forest(mod_b, slab =c(paste0(1:13,".", " ", K_b_sigma$Dataset)), 
       mlab = (paste("Random Effects Model Study 1-13 "))) 
summary(mod_b)
```

### Meta-Analysis b mean positive

```{r}
K_b_sigma$est.error_p_b_neuro <- as.numeric( K_b_sigma$est.error_p_b_neuro)
K_b_sigma$pos_b_neuro <- as.numeric( K_b_sigma$pos_b_neuro)

mod_b2 <-  rma(yi= pos_b_neuro, sei= est.error_p_b_neuro, data= K_b_sigma )  
forest(mod_b2, slab =c(paste0(1:13,".", " ", K_b_sigma$Dataset)), 
       mlab = (paste("Random Effects Model Study 1-13 ")))   
summary(mod_b2)

```

## RVI

### Meta-Analysis unweighted RVI negative

```{r}
K_RSD$neg_b_neuro_sigma<- as.numeric( K_RSD$neg_b_neuro_sigma)
K_RSD$est.error_n_b_neuro_sigma<- as.numeric( K_RSD$est.error_n_b_neuro_sigma)

K_RSD$pos_b_neuro<- as.numeric( K_RSD$pos_b_neuro)
K_RSD$est.error_p_b_neuro<- as.numeric( K_RSD$est.error_p_b_neuro)

#negative
mod_RSD <-  rma(yi= neg_b_neuro_sigma, vi= est.error_n_b_neuro_sigma, data= K_RSD )  
summary(mod_RSD)
forest(mod_RSD, slab =c(paste0(1:13,".", " ", K_b_sigma$Dataset)),xlim = c(-1.68, 1.58), at=seq(-0.6,0.6,by=.2),
       mlab = (paste("Random Effects Model Study 1-13 ")))
```
### Meta-Analysis unweighted RVI positive

```{r}
#positive
mod_RSDp <-  rma(yi= pos_b_neuro, vi= est.error_p_b_neuro, data= K_RSD )  
summary(mod_RSDp)
forest(mod_RSDp, slab =c(paste0(1:13,".", " ", K_b_sigma$Dataset)), 
       mlab = (paste("Random Effects Model Study 1-13 ")))
```

## RVI with weights 

### Meta-Analysis weighted RVI negative

```{r}
K_RSD_w$neg_b_neuro_sigma<- as.numeric( K_RSD_w$neg_b_neuro_sigma)
K_RSD_w$est.error_n_b_neuro_sigma<- as.numeric( K_RSD_w$est.error_n_b_neuro_sigma)

K_RSD_w$pos_b_neuro<- as.numeric( K_RSD_w$pos_b_neuro)                               
K_RSD_w$est.error_p_b_neuro<- as.numeric( K_RSD_w$est.error_p_b_neuro)


mod_RSD_w <-  rma(yi= neg_b_neuro_sigma, sei= est.error_n_b_neuro_sigma, data= K_RSD_w )  
summary(mod_RSD_w)
forest(mod_RSD_w, slab =c(paste0(1:13,".", " ", K_b_sigma$Dataset)),xlim = c(-1.68, 1.58), at=seq(-0.6,0.6,by=.2),
       mlab = (paste("Random Effects Model Study 1-13 ")))
```

### Meta-Analysis weighted RVI positive

```{r}
mod_RSD_w2 <-  rma(yi= pos_b_neuro, sei= est.error_p_b_neuro, data= K_RSD_w )  
summary(mod_RSD_w2)
forest(mod_RSD_w2, slab =c(paste0(1:13,".", " ", K_b_sigma$Dataset)), xlim = c(-0.4, 0.31), at=seq(-0.15,0.15,by=.05),
       mlab = (paste("Random Effects Model Study 1-13 ")))
```

## Gender Effects
```{r}
K_gender$neg_b_neuro <- as.numeric(K_gender$neg_b_neuro)
K_gender$est.error_n_b_neuro <- as.numeric(K_gender$est.error_n_b_neuro)

K_gender$neg_b_neuro_sigma <- as.numeric(K_gender$neg_b_neuro_sigma)
K_gender$est.error_n_b_neuro_sigma <- as.numeric(K_gender$est.error_n_b_neuro_sigma)


K_gender$b_neg_sigma_sex <- as.numeric(K_gender$b_neg_sigma_sex)
K_gender$est.error_b_neg_sigma_sex <- as.numeric(K_gender$est.error_b_neg_sigma_sex)


mod_sex1 <- rma(yi= b_neg_sigma_sex, sei= est.error_b_neg_sigma_sex, data= K_gender )
forest(mod_sex1, slab =paste(K_b_sigma$Dataset))  

mod_sex2 <- rma(yi= neg_b_neuro_sigma, sei= est.error_n_b_neuro_sigma, data= K_gender )
summary(mod_sex2)
forest(mod_sex2, slab =c(paste0(1:13,".", " ", K_b_sigma$Dataset)), 
       mlab = (paste("Random Effects Model Study 1-13* "))) 
mod_sex3 <- rma(yi= neg_b_neuro, sei= est.error_n_b_neuro, data= K_gender )
forest(mod_sex3, slab =c(paste0(1:13,".", " ", K_b_sigma$Dataset)), 
       mlab = (paste("Random Effects Model Study 1-13 ")))  
summary(mod_sex3)

```

