---
title: "MetaAnalysis"
output:
  html_document: 
    toc: yes
    number_sections: yes
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stringr)
library(metafor)
library(dplyr)
library(tidyverse)
library(readxl)
```

# Aggregate Results

```{r}
#create list with files from Kalokerinos Study
kalok_files = paste0("Dataset ", 1:11, " public.csv.xlsx")

# add Dataset 12  
kalok_files <- append(kalok_files, "results_wd.xlsx" )

#add Dataset 13
kalok_files <-  append(kalok_files, "results_LS.xlsx")

#read data
K_data <- lapply(kalok_files, read_excel)


# adding column with name of dataset
for( i in 1:13){
  
  K_data[[i]]$Dataset <- NA
}

for( i in 1:13){
  
  K_data[[i]]$Dataset <- rep(i, 7)
}

K_data <-  bind_rows(K_data) 

#add author names 

K_data$Dataset[K_data$Dataset == 1] <- "Van Ryckeghem et al."
K_data$Dataset[K_data$Dataset == 2] <- "Dejonckheere et al."
K_data$Dataset[K_data$Dataset == 3] <- "Kalokerinos et al."
K_data$Dataset[K_data$Dataset == 4] <- "Grommisch et al."
K_data$Dataset[K_data$Dataset == 5] <- "Erbas et al."
K_data$Dataset[K_data$Dataset == 6] <- "Brans et al."
K_data$Dataset[K_data$Dataset == 7] <- "Holland et al."
K_data$Dataset[K_data$Dataset == 8] <- "Koval et al."
K_data$Dataset[K_data$Dataset == 9] <- "Koval et al."
K_data$Dataset[K_data$Dataset == 10] <- "Dejonckheere et al."
K_data$Dataset[K_data$Dataset == 11] <- "Kalokerinos et al."
K_data$Dataset[K_data$Dataset == 12] <- "Denissen et al."
K_data$Dataset[K_data$Dataset == 13] <- "Own diary data"


K_data <-  bind_rows(K_data)
```

# Data Preparation

```{r}
### seperate columns in value, est.error and CI

K_data <- K_data %>% 
  tidyr::separate(negemo_b_neuro,                      
                  c("neg_b_neuro", "est.error_n_b_neuro", "KIn_b_neuro"), sep = " ")

K_data <-K_data %>% 
  tidyr::separate(negemo_b_neuro_sigma,                      
                  c("neg_b_neuro_sigma", "est.error_n_b_neuro_sigma", "KIn_b_neuro_sigma"), sep = " ")

K_data <-K_data %>% 
  tidyr::separate(posemo_b_neuro,                      
                  c("pos_b_neuro", "est.error_p_b_neuro", "KIp_b_neuro"), sep = " ")

K_data <-K_data %>% 
  tidyr::separate(posemo_b_neuro_sigma,                      
                  c("pos_b_neuro_sigma", "est.error_p_b_neuro_sigma", "KIp_b_neuro_sigma"), sep = " ")

K_data <-K_data %>% 
  tidyr::separate(b_neg_sigma_sex,                      
                  c("b_neg_sigma_sex", "est.error_b_neg_sigma_sex", "KIb_neg_sigma_sex"), sep = " ")


K_data <-K_data %>% 
  tidyr::separate(b_pos_sigma_sex,                      
                  c("b_pos_sigma_sex", "est.error_b_pos_sigma_sex", "KIb_pos_sigma_sex"), sep = " ")

# save Table 
library("writexl")

write_xlsx(K_data,"~/new_results2.xlsx")

## Filter Dataset for plots 
K_b_sigma <- K_data %>% filter(model== "model3")
K_RSD <- K_data %>% filter(model == "RSD")
K_RSD_w <- K_data %>% filter(model == "RSD_weight")
K_gender <- K_data %>% filter(model == "gender") 
K_SD <- K_data %>% filter(model == "SD") 

```

# Plot Data 

```{r}
apatheme = theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        panel.border = element_blank(),
        text=element_text(family='Arial'),
        legend.title=element_blank(),
        legend.position=c(.7,.8),
        axis.line.x = element_line(color='black'),
        axis.line.y = element_line(color='black'))
```

## BCLSM

### Meta-Analysis b sigma negative

```{r}
# 1. b sigma 
K_b_sigma$est.error_n_b_neuro_sigma <- as.numeric( K_b_sigma$est.error_n_b_neuro_sigma)
K_b_sigma$neg_b_neuro_sigma <- as.numeric( K_b_sigma$neg_b_neuro_sigma)

mod_b_sigma <-  rma(yi= neg_b_neuro_sigma, sei= est.error_n_b_neuro_sigma, data= K_b_sigma )  
summary(mod_b_sigma)
forest(mod_b_sigma, slab =c(paste0(1:13,".", " ", K_b_sigma$Dataset)),                        
       mlab = (paste("Random Effects Model Study 1-13 "))) 
par(bg="white")
```

### Meta-Analysis b sigma positive

```{r}
K_b_sigma$est.error_p_b_neuro_sigma <- as.numeric( K_b_sigma$est.error_p_b_neuro_sigma)
K_b_sigma$pos_b_neuro_sigma <- as.numeric( K_b_sigma$pos_b_neuro_sigma)

mod_b_sigma2 <-  rma(yi= pos_b_neuro_sigma, sei= est.error_p_b_neuro_sigma, data= K_b_sigma )  
summary(mod_b_sigma2)

pos_sigma <- forest(mod_b_sigma2, slab =c(paste0(1:13,".", " ", K_b_sigma$Dataset)), 
                    xlim=c(-0.6,0.6), at=seq(-0.2,0.3,by=.1),
                    mlab = (paste("Random Effects Model Study 1-13 "))) 
pos_sigma
```

### Meta-Analysis b mean negative

```{r}
# b mean 

K_b_sigma$est.error_n_b_neuro <- as.numeric( K_b_sigma$est.error_n_b_neuro)
K_b_sigma$neg_b_neuro <- as.numeric( K_b_sigma$neg_b_neuro)

mod_b <-  rma(yi= neg_b_neuro, sei= est.error_n_b_neuro, data= K_b_sigma )  
forest(mod_b, slab =c(paste0(1:13,".", " ", K_b_sigma$Dataset)), 
       mlab = (paste("Random Effects Model Study 1-13 "))) 
summary(mod_b)
```

### Meta-Analysis b mean positive

```{r}
K_b_sigma$est.error_p_b_neuro <- as.numeric( K_b_sigma$est.error_p_b_neuro)
K_b_sigma$pos_b_neuro <- as.numeric( K_b_sigma$pos_b_neuro)

mod_b2 <-  rma(yi= pos_b_neuro, sei= est.error_p_b_neuro, data= K_b_sigma )  
forest(mod_b2, slab =c(paste0(1:13,".", " ", K_b_sigma$Dataset)), 
       mlab = (paste("Random Effects Model Study 1-13 ")))   
summary(mod_b2)

```

## RVI

### Meta-Analysis unweighted RVI negative

```{r}
K_RSD$neg_b_neuro_sigma<- as.numeric( K_RSD$neg_b_neuro_sigma)
K_RSD$est.error_n_b_neuro_sigma<- as.numeric( K_RSD$est.error_n_b_neuro_sigma)

K_RSD$pos_b_neuro<- as.numeric( K_RSD$pos_b_neuro)
K_RSD$est.error_p_b_neuro<- as.numeric( K_RSD$est.error_p_b_neuro)

#negative
mod_RSD <-  rma(yi= neg_b_neuro_sigma, vi= est.error_n_b_neuro_sigma, data= K_RSD )  
summary(mod_RSD)
forest(mod_RSD, slab =c(paste0(1:13,".", " ", K_b_sigma$Dataset)),xlim = c(-1.68, 1.58), at=seq(-0.6,0.6,by=.2),
       mlab = (paste("Random Effects Model Study 1-13 ")))
```

### Meta-Analysis unweighted RVI positive

```{r}
#positive
mod_RSDp <-  rma(yi= pos_b_neuro, vi= est.error_p_b_neuro, data= K_RSD )  
summary(mod_RSDp)
forest(mod_RSDp, slab =c(paste0(1:13,".", " ", K_b_sigma$Dataset)), 
       mlab = (paste("Random Effects Model Study 1-13 ")))
```

## RVI with weights 

### Meta-Analysis weighted RVI negative

```{r}
K_RSD_w$neg_b_neuro_sigma<- as.numeric( K_RSD_w$neg_b_neuro_sigma)
K_RSD_w$est.error_n_b_neuro_sigma<- as.numeric( K_RSD_w$est.error_n_b_neuro_sigma)

K_RSD_w$pos_b_neuro<- as.numeric( K_RSD_w$pos_b_neuro)                               
K_RSD_w$est.error_p_b_neuro<- as.numeric( K_RSD_w$est.error_p_b_neuro)


mod_RSD_w <-  rma(yi= neg_b_neuro_sigma, sei= est.error_n_b_neuro_sigma, data= K_RSD_w )  
summary(mod_RSD_w)
forest(mod_RSD_w, slab =c(paste0(1:13,".", " ", K_b_sigma$Dataset)),xlim = c(-1.68, 1.58), at=seq(-0.6,0.6,by=.2),
       mlab = (paste("Random Effects Model Study 1-13 ")))
```

### Meta-Analysis weighted RVI positive

```{r}
mod_RSD_w2 <-  rma(yi= pos_b_neuro, sei= est.error_p_b_neuro, data= K_RSD_w )  
summary(mod_RSD_w2)
forest(mod_RSD_w2, slab =c(paste0(1:13,".", " ", K_b_sigma$Dataset)), xlim = c(-0.4, 0.31), at=seq(-0.15,0.15,by=.05),
       mlab = (paste("Random Effects Model Study 1-13 ")))
```

## Gender Effects

```{r}
K_gender$neg_b_neuro <- as.numeric(K_gender$neg_b_neuro)
K_gender$est.error_n_b_neuro <- as.numeric(K_gender$est.error_n_b_neuro)

K_gender$neg_b_neuro_sigma <- as.numeric(K_gender$neg_b_neuro_sigma)
K_gender$est.error_n_b_neuro_sigma <- as.numeric(K_gender$est.error_n_b_neuro_sigma)


K_gender$b_neg_sigma_sex <- as.numeric(K_gender$b_neg_sigma_sex)
K_gender$est.error_b_neg_sigma_sex <- as.numeric(K_gender$est.error_b_neg_sigma_sex)




mod_sex2 <- rma(yi= neg_b_neuro_sigma, sei= est.error_n_b_neuro_sigma, data= K_gender )
summary(mod_sex2)
forest(mod_sex2, slab =c(paste0(1:13,".", " ", K_b_sigma$Dataset)), 
       mlab = (paste("Random Effects Model Study 1-13* ")))
```


```{r}
mod_sex3 <- rma(yi= neg_b_neuro, sei= est.error_n_b_neuro, data= K_gender )
forest(mod_sex3, slab =c(paste0(1:13,".", " ", K_b_sigma$Dataset)), 
       mlab = (paste("Random Effects Model Study 1-13 ")))  
summary(mod_sex3)

```

## Model comparison

### censoring vs. no censoring 

#### no censoring (negative Emotion)

```{r include=FALSE}
#read in new data files
library(readxl)

Dat1 <- read_excel("Dataset 1 public.csvCENS.xlsx")
Dat2 <- read_excel("Dataset 2 public.csvCENS.xlsx")
Dat3 <- read_excel("Dataset 3 public.csvCENS.xlsx")
Dat4 <- read_excel("Dataset 4 public.csvCENS.xlsx")
Dat5 <- read_excel("Dataset 5 public.csvCENS.xlsx")
Dat6 <- read_excel("Dataset 6 public.csvCENS.xlsx")
Dat7 <- read_excel("Dataset 7 public.csvCENS.xlsx")
Dat8 <- read_excel("Dataset 8 public.csvCENS.xlsx")
Dat9 <- read_excel("Dataset 9 public.csvCENS.xlsx")
Dat10 <- read_excel("Dataset 10 public.csvCENS.xlsx")
Dat11<- read_excel("Dataset 11 public.csvCENS.xlsx")
Dat12 <- read_excel("results_wCENS.xlsx")
Dat13 <- read_excel("results_LSCENS.xlsx")

Censo <- full_join(x = Dat1, y = Dat2, by= c("model","negemo_b_neuro", "negemo_b_neuro_sigma", "negemo_sigma","posemo_b_neuro", "posemo_b_neuro_sigma", "posemo_sigma"))
Censo <- full_join(x = Censo, y = Dat3, by= c("model","negemo_b_neuro", "negemo_b_neuro_sigma", "negemo_sigma","posemo_b_neuro", "posemo_b_neuro_sigma", "posemo_sigma"))
Censo <- full_join(x = Censo, y = Dat4, by= c("model","negemo_b_neuro", "negemo_b_neuro_sigma", "negemo_sigma","posemo_b_neuro", "posemo_b_neuro_sigma", "posemo_sigma"))
Censo <- full_join(x = Censo, y = Dat5, by= c("model","negemo_b_neuro", "negemo_b_neuro_sigma", "negemo_sigma","posemo_b_neuro", "posemo_b_neuro_sigma", "posemo_sigma"))
Censo <- full_join(x = Censo, y = Dat6, by= c("model","negemo_b_neuro", "negemo_b_neuro_sigma", "negemo_sigma","posemo_b_neuro", "posemo_b_neuro_sigma", "posemo_sigma"))
Censo <- full_join(x = Censo, y = Dat7, by= c("model","negemo_b_neuro", "negemo_b_neuro_sigma", "negemo_sigma","posemo_b_neuro", "posemo_b_neuro_sigma", "posemo_sigma"))
Censo <- full_join(x = Censo, y = Dat8, by= c("model","negemo_b_neuro", "negemo_b_neuro_sigma", "negemo_sigma","posemo_b_neuro", "posemo_b_neuro_sigma", "posemo_sigma"))
Censo <- full_join(x = Censo, y = Dat9, by= c("model","negemo_b_neuro", "negemo_b_neuro_sigma", "negemo_sigma","posemo_b_neuro", "posemo_b_neuro_sigma", "posemo_sigma"))

Censo$Dataset <- rep(1:9, each=2)

Censo <- full_join(x = Censo, y = Dat10, by= c("model","negemo_b_neuro", "negemo_b_neuro_sigma", "negemo_sigma","posemo_b_neuro", "posemo_b_neuro_sigma", "posemo_sigma"))
Censo$Dataset[19] <- "10"
Censo$Dataset[20] <- "10"


Censo <- full_join(x = Censo, y = Dat11, by= c("model","negemo_b_neuro", "negemo_b_neuro_sigma", "negemo_sigma","posemo_b_neuro", "posemo_b_neuro_sigma", "posemo_sigma"))
Censo$Dataset[21] <- "11"
Censo$Dataset[22] <- "11"

Censo <- full_join(x = Censo, y = Dat12, by= c("model","negemo_b_neuro", "negemo_b_neuro_sigma", "negemo_sigma","posemo_b_neuro", "posemo_b_neuro_sigma", "posemo_sigma"))
Censo$Dataset[23] <- "12"
Censo$Dataset[24] <- "12"


Censo <- full_join(x = Censo, y = Dat13, by= c("model","negemo_b_neuro", "negemo_b_neuro_sigma", "negemo_sigma","posemo_b_neuro", "posemo_b_neuro_sigma", "posemo_sigma"))
Censo$Dataset[25] <- "13"
Censo$Dataset[26] <- "13"


Censo$Study <- NULL
Censo$negemo_sigma <- NULL
Censo$posemo_sigma <- NULL

Censo <- Censo %>% 
  tidyr::separate(negemo_b_neuro_sigma,                      
                  c("negemo_b_neuro_sigma", "est.error_b_neg_sigma", "KI_b_neg_sigma"), sep = " ")

Censo <- Censo %>% 
  tidyr::separate(negemo_b_neuro,                      
                  c("negemo_b_neuro", "est.error_b_neg", "KI_b_neg"), sep = " ")

write_xlsx(Censo,"~/Censo.xlsx")
```


```{r }
noC <- Censo %>% filter(model== "modelnoCensoring")


apatheme = theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        panel.border = element_blank(),
        text=element_text(family='Arial'),
        legend.title=element_blank(),
        legend.position=c(.7,.8),
        axis.line.x = element_line(color='black'),
        axis.line.y = element_line(color='black'))

names(noC)

noC$negemo_b_neuro_sigma<- as.numeric(noC$negemo_b_neuro_sigma)
noC$Dataset <- as.numeric(noC$Dataset)

noC$est.error_b_neg_sigma <- as.numeric(noC$est.error_b_neg_sigma)

noC$negemo_b_neuro<- as.numeric(noC$negemo_b_neuro)
noC$Dataset <- as.numeric(noC$Dataset)

noC$est.error_b_neg <- as.numeric(noC$est.error_b_neg)

# b sigma without censoring 
mod_b_sigma <-  rma(yi= negemo_b_neuro_sigma, sei= est.error_b_neg_sigma, data= noC )  
summary(mod_b_sigma)
forest(mod_b_sigma, slab =c(paste0("Study ", noC$Dataset)), 
       mlab = (paste("RE Model Study 1-13 ")))
```


```{r }
#b mean without censoring
mod_b_mean <-  rma(yi= negemo_b_neuro, sei= est.error_b_neg, data= noC )  
summary(mod_b_mean)
forest(mod_b_mean, slab =c(paste0("Study ", noC$Dataset)), 
       mlab = (paste("RE Model Study 1-13 "))) 

```

#### no censoring (positive Emotion) 

```{r}
CensoP <- Censo %>% 
  tidyr::separate(posemo_b_neuro_sigma,                      
                  c("pos_b_neuro_sigma", "est.error_b_pos_sigma", "KI_b_pos_sigma"), sep = " ")

CensoP <- CensoP %>% 
  tidyr::separate(posemo_b_neuro,                      
                  c("pos_b_neuro", "est.error_b_pos", "KI_b_pos"), sep = " ")

write_xlsx(CensoP,"~/CensoP.xlsx")


noCp <- CensoP %>% filter(model== "modelnoCensoring")
names(noCp)


noCp$pos_b_neuro_sigma<- as.numeric(noCp$pos_b_neuro_sigma)
noCp$Dataset <- as.numeric(noCp$Dataset)

noCp$est.error_b_pos_sigma <- as.numeric(noCp$est.error_b_pos_sigma)

#b sigma without censoring 
mod_b_sigmaP <-  rma(yi= pos_b_neuro_sigma, sei= est.error_b_pos_sigma, data= noCp )  
summary(mod_b_sigmaP)
forest(mod_b_sigmaP, slab =c(paste0("Study ", noCp$Dataset)), 
       mlab = (paste("RE Model Study 1-13 "))) 

```

### model C (two part)

#### negative Emotion 

```{r include=FALSE}
#read in new data tables
setwd("~/rstudio01/Neu")
Dat1 <- read_excel("Dataset 1 public.csvjinxed.xlsx")
Dat2 <- read_excel("Dataset 2 public.csvjinxed.xlsx")
Dat3 <- read_excel("Dataset 3 public.csvjinxed.xlsx")
Dat4 <- read_excel("Dataset 4 public.csvjinxed.xlsx")
Dat5 <- read_excel("Dataset 5 public.csvjinxed.xlsx")
Dat6 <- read_excel("Dataset 6 public.csvjinxed.xlsx")
Dat7 <- read_excel("Dataset 7 public.csvjinxed.xlsx")
Dat8 <- read_excel("Dataset 8 public.csvjinxed.xlsx")
Dat9 <- read_excel("Dataset 9 public.csvjinxed.xlsx")
Dat10 <- read_excel("Dataset 10 public.csvjinxed.xlsx")
Dat11<- read_excel("Dataset 11 public.csvjinxed.xlsx")
Dat12 <- read_excel("results_wquant.xlsx")
Dat13 <- read_excel("results_LSquant.xlsx")

quant <- full_join(x = Dat1, y = Dat2, by= c("model","negemo_b_neuro","negemo_b_neuro_sigma", "negemo_sigma"))
quant <- full_join(x = quant, y = Dat3, by= c("model","negemo_b_neuro","negemo_b_neuro_sigma", "negemo_sigma"))
quant <- full_join(x = quant, y = Dat4, by= c("model","negemo_b_neuro","negemo_b_neuro_sigma", "negemo_sigma"))
quant <- full_join(x = quant, y = Dat5, by= c("model","negemo_b_neuro","negemo_b_neuro_sigma", "negemo_sigma"))
quant <- full_join(x = quant, y = Dat6, by= c("model","negemo_b_neuro","negemo_b_neuro_sigma", "negemo_sigma"))
quant <- full_join(x = quant, y = Dat7, by= c("model","negemo_b_neuro","negemo_b_neuro_sigma", "negemo_sigma"))
quant <- full_join(x = quant, y = Dat8, by= c("model","negemo_b_neuro","negemo_b_neuro_sigma", "negemo_sigma"))
quant <- full_join(x = quant, y = Dat9, by= c("model","negemo_b_neuro","negemo_b_neuro_sigma", "negemo_sigma"))

quant$Study <- rep(1:9, each=2)
quant <- full_join(x = quant, y = Dat10, by= c("model","negemo_b_neuro","negemo_b_neuro_sigma", "negemo_sigma"))
quant$Study[19] <- "10"
quant$Study[20] <- "10"


quant <- full_join(x = quant, y = Dat11, by= c("model","negemo_b_neuro","negemo_b_neuro_sigma", "negemo_sigma"))
quant$Study[21] <- "11"
quant$Study[22] <- "11"
quant <- full_join(x = quant, y = Dat12, by= c("model","negemo_b_neuro","negemo_b_neuro_sigma", "negemo_sigma"))
quant <- full_join(x = quant, y = Dat13, by= c("model","negemo_b_neuro","negemo_b_neuro_sigma", "negemo_sigma"))
quant$Study[23] <- "12"
quant$Study[24] <- "12"
quant$Study[25] <- "13"
quant$Study[26] <- "13"

quant <- quant %>% 
  tidyr::separate(negemo_b_neuro,                      
                  c("b_neuro", "est.error_b_neuro", "KI_b_neuro"), sep = " ")

quant <- quant %>% 
  tidyr::separate(negemo_b_neuro_sigma,                      
                  c("b_neuro_sigma", "est.error_b_neuro_sigma", "KI_b_neuro_sigma"), sep = " ")

write_xlsx(quant,"~/quant.xlsx")
```


```{r}
#Exclude study 11 

quant <- quant[-c(21:22),]

apatheme = theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        panel.border = element_blank(),
        text=element_text(family='Arial'),
        legend.title=element_blank(),
        legend.position=c(.7,.8),
        axis.line.x = element_line(color='black'),
        axis.line.y = element_line(color='black'))

names(quant)

quant$b_neuro_sigma <- as.numeric(quant$b_neuro_sigma)
quant$Study <- as.numeric(quant$Study)

quant$est.error_b_neuro_sigma <- as.numeric(quant$est.error_b_neuro_sigma)
quant$b_neuro <- as.numeric(quant$b_neuro)
quant$est.error_b_neuro <- as.numeric(quant$est.error_b_neuro)

quant2 <- quant %>% filter(model== "BCSLM_q")


#b sigma two part model C:
mod_b_sigma <-  rma(yi= b_neuro_sigma, sei= est.error_b_neuro_sigma, data= quant2 )  
summary(mod_b_sigma)
forest(mod_b_sigma, slab =c(paste0("Study ", quant2$Study)), 
       mlab = (paste("RE Model Study 1-13 ")))
```


```{r}
#b mean two part model C:
mod_b_mean <-  rma(yi= b_neuro, sei= est.error_b_neuro, data= quant2 )  
summary(mod_b_mean)
forest(mod_b_mean, slab =c(paste0("Study ", quant2$Study)), 
       mlab = (paste("RE Model Study 1-13 "))) 

```

#### positive Emotion 

```{r include=FALSE}
library(readxl)

Dat1 <- read_excel("Dataset 1 public.csvjinxedPO.xlsx")
Dat2 <- read_excel("Dataset 2 public.csvjinxedPO.xlsx")
Dat3 <- read_excel("Dataset 3 public.csvjinxedPO.xlsx")
Dat4 <- read_excel("Dataset 4 public.csvjinxedPO.xlsx")
Dat5 <- read_excel("Dataset 5 public.csvjinxedPO.xlsx")
Dat6 <- read_excel("Dataset 6 public.csvjinxedPO.xlsx")
Dat7 <- read_excel("Dataset 7 public.csvjinxedPO.xlsx")
Dat8 <- read_excel("Dataset 8 public.csvjinxedPO.xlsx")
Dat9 <- read_excel("Dataset 9 public.csvjinxedPO.xlsx")
Dat10 <- read_excel("Dataset 10 public.csvjinxedPO.xlsx")
Dat11<- read_excel("Dataset 11 public.csvjinxedPO.xlsx")
Dat12 <- read_excel("results_wquantPO.xlsx")
Dat13 <- read_excel("results_LSquantPO.xlsx")

quant <- full_join(x = Dat1, y = Dat2, by= c("model","posemo_b_neuro","posemo_b_neuro_sigma", "posemo_sigma"))
quant <- full_join(x = quant, y = Dat3, by= c("model","posemo_b_neuro","posemo_b_neuro_sigma", "posemo_sigma"))
quant <- full_join(x = quant, y = Dat4, by= c("model","posemo_b_neuro","posemo_b_neuro_sigma", "posemo_sigma"))
quant <- full_join(x = quant, y = Dat5, by= c("model","posemo_b_neuro","posemo_b_neuro_sigma", "posemo_sigma"))
quant <- full_join(x = quant, y = Dat6, by= c("model","posemo_b_neuro","posemo_b_neuro_sigma", "posemo_sigma"))
quant <- full_join(x = quant, y = Dat7, by= c("model","posemo_b_neuro","posemo_b_neuro_sigma", "posemo_sigma"))
quant <- full_join(x = quant, y = Dat8, by= c("model","posemo_b_neuro","posemo_b_neuro_sigma", "posemo_sigma"))
quant <- full_join(x = quant, y = Dat9, by= c("model","posemo_b_neuro","posemo_b_neuro_sigma", "posemo_sigma"))

quant$Study <- rep(1:9, each=2)
quant <- full_join(x = quant, y = Dat10, by= c("model","posemo_b_neuro","posemo_b_neuro_sigma", "posemo_sigma"))
quant$Study[19] <- "10"
quant$Study[20] <- "10"


quant <- full_join(x = quant, y = Dat11, by= c("model","posemo_b_neuro","posemo_b_neuro_sigma", "posemo_sigma"))
quant$Study[21] <- "11"
quant$Study[22] <- "11"
quant <- full_join(x = quant, y = Dat12, by= c("model","posemo_b_neuro","posemo_b_neuro_sigma", "posemo_sigma"))
quant <- full_join(x = quant, y = Dat13, by= c("model","posemo_b_neuro","posemo_b_neuro_sigma", "posemo_sigma"))
quant$Study[23] <- "12"
quant$Study[24] <- "12"
quant$Study[25] <- "13"
quant$Study[26] <- "13"

names(quant)
quant <- quant %>% 
  tidyr::separate(posemo_b_neuro,                      
                  c("b_neuro", "est.error_b_neuro", "KI_b_neuro"), sep = " ")

quant <- quant %>% 
  tidyr::separate(posemo_b_neuro_sigma,                      
                  c("b_neuro_sigma", "est.error_b_neuro_sigma", "KI_b_neuro_sigma"), sep = " ")
```

```{r}
#exclude study 2 and 3
quant <- quant[-c(3:6),]

quant$b_neuro_sigma <- as.numeric(quant$b_neuro_sigma)
quant$Study <- as.numeric(quant$Study)

quant$est.error_b_neuro_sigma <- as.numeric(quant$est.error_b_neuro_sigma)
quant$b_neuro <- as.numeric(quant$b_neuro)
quant$est.error_b_neuro <- as.numeric(quant$est.error_b_neuro)

quant2 <- quant %>% filter(model== "BCSLM_q")

#b sigma two part model C:
mod_b_sigma <-  rma(yi= b_neuro_sigma, sei= est.error_b_neuro_sigma, data= quant2 )  
summary(mod_b_sigma)
forest(mod_b_sigma, slab =c(paste0("Study ", quant2$Study)), 
       mlab = (paste("RE Model Study 1-13 ")))
```


```{r}
#b mean two part model C:
mod_b_mean <-  rma(yi= b_neuro, sei= est.error_b_neuro, data= quant2 )  
summary(mod_b_mean)
forest(mod_b_mean, slab =c(paste0("Study ", quant2$Study)), 
       mlab = (paste("RE Model Study 1-13 "))) 

```

