---
title: "Dataset 13"
author: 
output:
  html_document: 
    toc: yes
    number_sections: yes
---

```{r, include=FALSE }
library(psych)
library(relativeVariability)
library(brms)
library(cmdstanr)
library(data.table)
library(ggplot2)
library(dplyr)
library(remotes)
library(loo)
library(knitr)
library(rstan)
library(shinystan)

options(mc.cores = 8, brms.backend = "cmdstanr", brms.file_refit = "on_change")


Daily <- read.csv("~/rstudio01/Neu/MA/Daily.csv", header=TRUE)
Start <- read.csv("~/rstudio01/Neu/MA/Start.csv", header=TRUE)

items_pa <- c("PA_S_1", "PA_S_2", "PA_S_3")
items_na <- c("NA_S_1", "NA_S_2", "NA_S_3", "NA_S_4", "NA_S_5")

#Aggregate 
Daily$pa <- rowMeans(Daily[, items_pa])
Daily$na <- rowMeans(Daily[, items_na])

mean(Daily$na, na.rm=T)
mean(Daily$pa, na.rm=T)
range(Daily$pa, na.rm=T)
qplot(Daily$pa, binwidth = 0.1)

#Neuroticism
Start$BFI_NEU_1 <- NA
Start$BFI_NEU_1 <- 5 + 1 - Start$BFI_NEU_1_R
Start$BFI_NEU_1_R <- NULL

Start$BFI_NEU_2 <- 5 + 1 - Start$BFI_NEU_2_R 
Start$BFI_NEU_2_R <- NULL

Start$BFI_NEU_3 <- 5 + 1 - Start$BFI_NEU_3_R
Start$BFI_NEU_3_R <- NULL

# BFI Data to calculate neuroticism score

BFI_NEU <- data.frame(session = Start$session,
                      BFI_NEU_1 = Start$BFI_NEU_1,
                      BFI_NEU_2 = Start$BFI_NEU_2,
                      BFI_NEU_3 = Start$BFI_NEU_3,
                      BFI_NEU_4 = Start$BFI_NEU_4,
                      BFI_NEU_5 = Start$BFI_NEU_5,
                      BFI_NEU_6 = Start$BFI_NEU_6)

# Check for neuroticism
mean(BFI_NEU$session == Start$session)

# BFI_NEU
describe(BFI_NEU[, -1])
psych::alpha(BFI_NEU[, -1]) 

#Neuroticism score

BFI_NEU$BFI_NEU <- rowMeans(BFI_NEU[, -1]) 

# bind to Start
Start$Neurot <- BFI_NEU$BFI_NEU

#bind to daily
daily <- merge(Daily, BFI_NEU, all.x = T, by= "session")

daily <- daily %>% group_by(session) %>% filter(n()>= 5) %>% ungroup()

daily$neurot <- daily$BFI_NEU
```

# Data Preparation

#Plot Affect

```{r}
ggplot(daily, aes(na)) +
  geom_histogram(binwidth = 0.1) + 
  ggtitle("Distribution of Negative Emotion Study 13") +
  xlab("Negative Emotion") + ylab("Frequency") + 
  scale_x_continuous(breaks = seq(1, 5, 1)) +
  scale_y_continuous(breaks = seq(0, 1000, 200)) +
  theme(text = element_text(size = 10, family = "Times New Roman"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black")) +
  coord_cartesian(xlim = c(1, 5), ylim = c(0, 1000))

ggsave("NAS13.png", width = 4, height = 3)


ggplot(daily, aes(pa)) +
  geom_histogram(binwidth = 0.1) + 
  ggtitle("Distribution of Positive Emotion Study 13") +
  xlab("Positive Emotion") + ylab("Frequency") + 
  scale_x_continuous(breaks = seq(1, 5, 1)) +
  scale_y_continuous(breaks = seq(0, 1500, 200)) +
  theme(text = element_text(size = 10, family = "Times New Roman"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black")) +
  coord_cartesian(xlim = c(1, 5), ylim = c(0, 1200))

ggsave("PAS13.png", width = 4, height = 3)
```

## Censoring 

```{r}
daily$Acens <- case_when(daily$na == 1 ~ "left",
                         daily$na == 5 ~ "right",
                         TRUE ~ "none")
table(daily$Acens)

daily$Acensp <- case_when(daily$pa == 1 ~ "left",
                         daily$pa == 5 ~ "right",
                         TRUE ~ "none")
table(daily$Acensp)
```

# BCLSM Negative Emotion

```{r message=TRUE, warning=TRUE}
na_model_neuro3 <- brm(bf(na | cens(Acens) ~ neurot + (1|session),
                       sigma ~ neurot + (1|session)), data = daily,
                       iter = 7000, warmup = 2000,chains = 8, init = 0.1,
                      control = list(adapt_delta = .99),
                   file = "na_model_neuro3")
print(na_model_neuro3)
plot(na_model_neuro3)
prior_summary(na_model_neuro3)


```

## Model comparison 
### scale vs. no scale parameter

```{r}

na_model_neuro2 <- brm(na | cens(Acens) ~ neurot + (1|session), data = daily,
                    iter = 3000, warmup = 1000, chains = 8,
                   file = "na_model_neuro2")
print(na_model_neuro2)
plot(na_model_neuro2)
```

```{r message=TRUE, warning=TRUE}
modelA <- na_model_neuro2
modelB <- na_model_neuro3

modelA <- add_criterion(modelA, "loo")
modelB <- add_criterion(modelB, "loo")

loo <- loo_compare(modelA,modelB, criterion = "loo")

loo <- as.data.frame(loo)

loo$Dataset <- "13"
loo <- tibble::rownames_to_column(loo, "model")

library("writexl")
write_xlsx(loo,"~/looDataset13.xlsx")
kable(loo)

```

### censoring vs. no censoring 

```{r}
na_model_neuro4 <- brm(bf(na  ~ neurot + (1|session),
                       sigma ~ neurot + (1|session)), data = daily,
                       iter = 7000, warmup = 2000,chains = 4, init = 0.1,
                      control = list(adapt_delta = .99),
                   file = "na_model_neuro4")

print(na_model_neuro4)
```

```{r}
extract_param <- function(model, parameter) {
  ci <- posterior_summary(model, variable = parameter)
  est <- sprintf("%.2f %.2f [%.2f;%.2f]", ci[,"Estimate"],ci[,"Est.Error"], ci[,"Q2.5"], ci[,"Q97.5"])
  est
}

results_LScens <- data.frame(matrix(nrow = 2, # Modelle & RVI 
                             ncol = 6+1)) # 2 Affekte a 3 Spalten 
names(results_LScens) <- c("model", "negemo_b_neuro", "negemo_b_neuro_sigma", "negemo_sigma",
                    "posemo_b_neuro", "posemo_b_neuro_sigma", "posemo_sigma"
                    )

results_LScens$model <- c("modelCensoring", "modelnoCensoring")

#NA

results_LScens[1, "negemo_b_neuro"] <- extract_param(na_model_neuro3, "b_neurot")
results_LScens[1, "negemo_b_neuro_sigma"] <- extract_param(na_model_neuro3, "b_sigma_neurot")
results_LScens[1, "negemo_sigma"] <- extract_param(na_model_neuro3, "b_sigma_Intercept")

results_LScens[2, "negemo_b_neuro"] <- extract_param(na_model_neuro4, "b_neurot")
results_LScens[2, "negemo_b_neuro_sigma"] <- extract_param(na_model_neuro4, "b_sigma_neurot")
results_LScens[2, "negemo_sigma"] <- extract_param(na_model_neuro4, "b_sigma_Intercept")

```

### BCLSM vs. model C (two-part model)

```{r}
daily <- daily %>% left_join(daily %>% distinct(session, neurot) %>% mutate(neuro_Q =Hmisc::cut2(neurot, g = 4)), by = c("session", "neurot"))


na_model_neuro_jinxed <- brm(bf(na | cens(Acens) ~ neurot + (1|gr(session, by = neuro_Q)),
     sigma ~ neurot + (1|session)), data = daily,
  iter = 5000, warmup = 2000,  chains = 4,
  control = list(adapt_delta = .95), init = 0.1,
                   file = "na_model_neuro3_jinxed")


print(na_model_neuro_jinxed)

```

```{r}

modelA <- na_model_neuro3
modelB <- na_model_neuro_jinxed

modelA <- add_criterion(modelA, "loo")
modelB <- add_criterion(modelB, "loo")

loo_c <- loo_compare(modelA,modelB, criterion = "loo")

loo_c <- as.data.frame(loo)

loo_c$Dataset <- "13"
#loo_c <- tibble::rownames_to_column(loo, "model")
library("writexl")
write_xlsx(loo_c,"~/Study13loojinxed.xlsx")

kable(loo_c)
```

## control for gender

```{r}
table(Start$sex)

#1=female, 2=male, 3=diverse 
gender <- select(Start, session, sex)

# bins sex  to daily 
daily2 <- merge(daily, gender, all.x = T, by= "session")

daily2$sex <- as.numeric(daily2$sex)

## not enough diverse people to compare them (excluded from model) 
daily2$sex[daily2$sex == 3] <- NA
daily2$sex[daily2$sex == 2] <- 0


daily2$sex <- as.factor(daily2$sex)

table(daily2$sex, exclude = NULL)
```


```{r}
m3n_gender <- brm(bf(na | cens(Acens) ~ neurot+ sex + (1|session),
                       sigma ~ neurot+sex + (1|session)), data = daily2,
                       iter = 5000, warmup = 2000,chains = 4,
                      control = list(adapt_delta = .95), inits = 0.1,                
                  file = "m3n_gender")
print(m3n_gender)
```


# BCLSM Positive Emotion

```{r message=TRUE, warning=TRUE}


pa_model_neuro3 <- brm(bf(pa | cens(Acensp) ~ neurot + (1|session),
                       sigma ~ neurot + (1|session)), data = daily,
                        control = list(adapt_delta = .99),chains = 8,
                       iter = 5000, warmup = 2000,
                   file = "pa_model_neuro3")
print(pa_model_neuro3)
plot(pa_model_neuro3)
prior_summary(pa_model_neuro3)

pp_check(pa_model_neuro3)

```

## Model comparison 
### scale vs. no scale parameter

```{r}
pa_model_neuro2 <- brm(pa | cens(Acensp) ~ neurot + (1|session), data = daily,
                    iter = 4000, warmup = 1000, chains = 8,
                   file = "pa_model_neuro2")
print(pa_model_neuro2)
plot(pa_model_neuro2)
```

```{r}
modelAp <- pa_model_neuro2
modelBp <- pa_model_neuro3


modelAp <- add_criterion(modelAp, "loo")
modelBp <- add_criterion(modelBp, "loo")

looP <- loo_compare(modelAp,modelBp, criterion = "loo")

looP <- as.data.frame(looP)

looP$Dataset <- "13"
#looP <- tibble::rownames_to_column(looP, "model")
library("writexl")
write_xlsx(looP,"~/looPDataset13.xlsx")

kable(looP)
```

### censoring vs. no censoring 

```{r}
pa_model_neuro4 <- brm(bf(pa  ~ neurot + (1|session),
                       sigma ~ neurot + (1|session)), data = daily,
                        control = list(adapt_delta = .99),chains = 4,
                       iter = 5000, warmup = 2000,
                   file = "pa_model_neuro4")
print(pa_model_neuro4)
```

```{r}
results_LScens[1, "posemo_b_neuro"] <- extract_param(pa_model_neuro3, "b_neurot")
results_LScens[1, "posemo_b_neuro_sigma"] <- extract_param(pa_model_neuro3, "b_sigma_neurot")
results_LScens[1, "posemo_sigma"] <- extract_param(pa_model_neuro3, "b_sigma_Intercept")


results_LScens[2, "posemo_b_neuro"] <- extract_param(pa_model_neuro4, "b_neurot")
results_LScens[2, "posemo_b_neuro_sigma"] <- extract_param(pa_model_neuro4, "b_sigma_neurot")
results_LScens[2, "posemo_sigma"] <- extract_param(pa_model_neuro4, "b_sigma_Intercept")


library("writexl")
write_xlsx(results_LScens,"~/results_LSCENS.xlsx")
```

### BCLSM vs. model C (two-part model)


```{r}
pa_model_neuro_jinxed <- brm(bf(pa | cens(Acens) ~ neurot + (1|gr(session, by = neuro_Q)),
     sigma ~ neurot + (1|session)), data = daily,
  iter = 5000, warmup = 2000,  chains = 4,
  control = list(adapt_delta = .95), init = 0.1,
                   file = "pa_model_neuro3_jinxed")


print(pa_model_neuro_jinxed)
```

```{r message=TRUE, warning=TRUE}

modelA <- pa_model_neuro3
modelB <- pa_model_neuro_jinxed

modelA <- add_criterion(modelA, "loo")
modelB <- add_criterion(modelB, "loo")

loo_cP <- loo_compare(modelA,modelB, criterion = "loo")

loo_cP <- as.data.frame(loo)

loo_cP$Dataset <- "13"
#loo_cP <- tibble::rownames_to_column(loo_cP, "model")

library("writexl")
write_xlsx(loo_cP,"~/Study13POloojinxed.xlsx")

kable(loo_cP)
```

```{r}
extract_param <- function(model, parameter) {
  ci <- posterior_summary(model, variable = parameter)
  est <- sprintf("%.2f %.2f [%.2f;%.2f]", ci[,"Estimate"],ci[,"Est.Error"], ci[,"Q2.5"], ci[,"Q97.5"])
  est
}

results_LS <- data.frame(matrix(nrow = 7, # Modelle & RVI 
                             ncol = 8+1)) # 2 Affekte a 3 Spalten 
names(results_LS) <-c("model", "negemo_b_neuro", "negemo_b_neuro_sigma", "negemo_sigma", "b_neg_sigma_sex",
                    "posemo_b_neuro", "posemo_b_neuro_sigma", "posemo_sigma", "b_pos_sigma_sex"
                    )

results_LS$model <- c("model1", "model2", "model3",
                  "RSD", "RSD_weight", "SD", "gender")

#NA
results_LS[2, "negemo_b_neuro"] <- extract_param(na_model_neuro2, "b_neurot")
results_LS[2, "negemo_sigma"] <- extract_param(na_model_neuro2, "sigma")

results_LS[3, "negemo_b_neuro"] <- extract_param(na_model_neuro3, "b_neurot")
results_LS[3, "negemo_b_neuro_sigma"] <- extract_param(na_model_neuro3, "b_sigma_neurot")
results_LS[3, "negemo_sigma"] <- extract_param(na_model_neuro3, "b_sigma_Intercept")


#pa
results_LS[2, "posemo_b_neuro"] <- extract_param(pa_model_neuro2, "b_neurot")
results_LS[2, "posemo_sigma"] <- extract_param(pa_model_neuro2, "sigma")

results_LS[3, "posemo_b_neuro"] <- extract_param(pa_model_neuro3, "b_neurot")
results_LS[3, "posemo_b_neuro_sigma"] <- extract_param(pa_model_neuro3, "b_sigma_neurot")
results_LS[3, "posemo_sigma"] <- extract_param(pa_model_neuro3, "b_sigma_Intercept")

#gender
results_LS[7, "negemo_b_neuro"] <- extract_param(m3n_gender, "b_neurot")
results_LS[7, "negemo_b_neuro_sigma"] <- extract_param(m3n_gender, "b_sigma_neurot")
results_LS[7, "negemo_sigma"] <- extract_param(m3n_gender, "b_sigma_Intercept")
results_LS[7, "b_neg_sigma_sex"] <- extract_param(m3n_gender, "b_sigma_sex1")

```

# RVI (Relative-Variability-Index)
## Unweighted RVI

```{r message=TRUE, warning=TRUE}
#id <- unique(daily$session)
#id <- as.data.frame(id)

Start$RSD_NA <- NA
for (i in 1:nrow(Start)) {
  # aktuelle Zeilennummer
  if (Start$session[i] %in% Daily$session) {
    if (
      sum(!is.na(Daily$na[Daily$session == Start$session[i]])) >= 5
    ) { 
      Start$RSD_NA[i] <- relativeSD(Daily$na[Daily$session == Start$session[i]],
                                     1, 5)
    }
  } 
}


Start$logrsd_n <- log(Start$RSD_NA)
m_rsd_na <- brm(logrsd_n ~ Neurot, data= Start,
                file = "na_logrsd_uw")
print(m_rsd_na)

results_LS[4,3] <- extract_param(m_rsd_na, "b_Neurot")


Start$RSD_PA <- NA
for (i in 1:nrow(Start)) {
  # aktuelle Zeilennummer
  if (Start$session[i] %in% Daily$session) {
    if (
      sum(!is.na(Daily$pa[Daily$session == Start$session[i]])) >= 5
    ) { 
      Start$RSD_PA[i] <- relativeSD(Daily$pa[Daily$session == Start$session[i]],
                                     1, 5)
    }
  } 
}

Start$RSD_PA[Start$RSD_PA == 0] <- NA     # sonst log(0) = - Inf

Start$logrsd_p <- log(Start$RSD_PA)
range(Start$logrsd_p, na.rm = T)

m_rsd_pa <- brm(logrsd_p ~ Neurot, data= Start,
                file = "pa_logrsd_uw")
print(m_rsd_pa)

results_LS[4,6] <- extract_param(m_rsd_pa, "b_Neurot")

```

## Weighted RVI 

```{r message=TRUE, warning=TRUE}
Start$mean_NA <- NA
for (i in 1:nrow(Start)) {
  if (Start$session[i] %in% Daily$session) {
    if (
      sum(!is.na(Daily$na[Daily$session == Start$session[i]])) >= 5
    ) { 
      Start$mean_NA[i] <- mean(Daily$na[Daily$session == Start$session[i]],
                                   na.rm = T)
    }
  } 
}


Start$mean_PA <- NA
for (i in 1:nrow(Start)) {
  if (Start$session[i] %in% Daily$session) {
    if (
      sum(!is.na(Daily$pa[Daily$session == Start$session[i]])) >= 5
    ) { 
      Start$mean_PA[i] <- mean(Daily$pa[Daily$session == Start$session[i]],
                                   na.rm = T)
    }
  } 
}
```


```{r message=TRUE, warning=TRUE}

Start$weight_NA <- NA
for (i in 1:nrow(Start)) {
  if (Start$session[i] %in% Daily$session) {
  
    
    if (!is.na(Start$mean_NA[i])) {
      # If mean is not missing
      Start$weight_NA[i] <- maximumSD(Start$mean_NA[i], # mean
                                       1,  # min
                                       5,  # max
                                       sum(!is.na(Daily$na[Daily$session == Start$session[i]])) 
      ) 
      # W as reported in paper
      Start$weight_NA[i] <- Start$weight_NA[i]^2
    }
  }
}

m_rsd_na_w <- brm(logrsd_n| weights(weight_NA) ~ Neurot, data= Start,
                  file = "na_logrsd_w")
print(m_rsd_na_w)
results_LS[5,3] <- extract_param(m_rsd_na_w, "b_Neurot")



Start$weight_PA <- NA
for (i in 1:nrow(Start)) {
  if (Start$session[i] %in% Daily$session) {
  
    
    if (!is.na(Start$mean_PA[i])) {
      Start$weight_PA[i] <- maximumSD(Start$mean_PA[i],
                                       1,  
                                       5,  
                                       sum(!is.na(Daily$pa[Daily$session == Start$session[i]])) 
      ) 
      Start$weight_PA[i] <- Start$weight_PA[i]^2
    }
  }
}

m_rsd_Pa_w <- brm(logrsd_p| weights(weight_PA) ~ Neurot, data= Start,
                  file = "pa_logrsd_w")
print(m_rsd_Pa_w)
results_LS[5,6] <- extract_param(m_rsd_Pa_w, "b_Neurot")

```

# SD 

```{r}
Start$sd_NA <- NA
for (i in 1:nrow(Start)) {
  if (Start$session[i] %in% Daily$session) {
    if (
      sum(!is.na(Daily$na[Daily$session == Start$session[i]])) >= 5
    ) { 
      Start$sd_NA[i] <- sd(Daily$na[Daily$session == Start$session[i]],
                                   na.rm = T)
    }
  }
}

Start$sd_PA <- NA
for (i in 1:nrow(Start)) {
  if (Start$session[i] %in% Daily$session) {
    if (
      sum(!is.na(Daily$pa[Daily$session == Start$session[i]])) >= 5
    ) { 
      Start$sd_PA[i] <- sd(Daily$pa[Daily$session == Start$session[i]],
                                   na.rm = T)
    }
  }
}


mean(Start$sd_NA, na.rm = T)
mean(Start$sd_PA, na.rm= T)

Start$sd_PA[Start$sd_PA == 0] <- NA   

Start$logsd_NA <- log(Start$sd_NA)
Start$logsd_PA <- log(Start$sd_PA)

m_sd_na <- brm(logsd_NA ~ Neurot, data= Start,
               file = "na_logsd")
m_sd_na
results_LS[6,3] <- extract_param(m_sd_na, "b_Neurot")

m_sd_pa <- brm(logsd_PA ~ Neurot, data= Start,
               file = "pa_logsd")
m_sd_pa
results_LS[6,6] <- extract_param(m_sd_pa, "b_Neurot")

```



# Incremental Validity of SD 

```{r message=F, warning=F, silent=2}
na_noneurot <- brm(bf(na | cens(Acens) ~  (1|session),
                       sigma ~  (1|session)), data = daily,
                       iter = 7000, warmup = 2000,chains = 4,
                      control = list(adapt_delta = .99), init = 0.1,
                      file = "na_noneurot13")

print(na_noneurot)

rans <- coef(na_noneurot, summary = T)

rans_i <- as.data.frame(rans$session[,,"Intercept"]) %>% tibble::rownames_to_column("session")
rans_s <- as.data.frame(rans$session[,,"sigma_Intercept"]) %>% tibble::rownames_to_column("session")
nrow(rans_s)
nrow(rans_i)
nrow(Start)
dat <- merge(rans_s, rans_i, all = T, by= "session")
dat <- merge(dat, Start, all = T, by= "session")
names(dat)[2] <- "Est.SD"
names(dat)[6] <- "Est.M"

fit1 <- lm(Neurot ~ Est.SD + Est.M , data=dat)
summary(fit1)

fit1.2 <- lm(Neurot ~  Est.M , data=dat)
summary(fit1.2)

aov <- anova(fit1.2, fit1)
aov

summary(fit1)$r.squared-summary(fit1.2)$r.squared

results_SDin <- data.frame(matrix(nrow = 1, ncol = 9))
names(results_SDin) <- c("Dataset","b_SD","Err.SD","p(b_SD)","b_M","Err.M","p(b_M)","ΔR²", "p")

results_SDin$Dataset <- "13"

results_SDin$`ΔR²` <- summary(fit1)$r.squared-summary(fit1.2)$r.squared
results_SDin$`p` <- aov$`Pr(>F)`[2]
results_SDin$Err.SD <- summary(fit1)$coefficients[2,2]
results_SDin$b_SD <- fit1$coefficients[2]

results_SDin$`p(b_SD)` <- summary(fit1)$coefficients[2,4]
results_SDin$b_M <- fit1$coefficients[3]
results_SDin$`p(b_M)` <- summary(fit1)$coefficients[3,4]
results_SDin$Err.M <- summary(fit1)$coefficients[3,2]



library("writexl")
write_xlsx(results_SDin,"~/results_SD13.xlsx")

```

