---
title: "Additional Simulation with different Priors"
output:
  html_document: 
    toc: yes
    number_sections: yes
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(tidyverse)
library(tidybayes)
library(psych)
library(distributional)
library(ggdist )
#install.packages("~/rstudio01/Neu/relativeVariability_1.0.tar.gz", repos = NULL, type = "source")


library(relativeVariability)
library(brms)
library(cmdstanr)

options(mc.cores = parallel::detectCores(), brms.backend = "cmdstanr", brms.file_refit = "on_change")
#rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())

getwd()
setwd("/home/sc.uni-leipzig.de/no628luhi/prior")
#run parallel cores 
options(mc.cores = parallel::detectCores(), brms.backend = "cmdstanr", brms.file_refit = "on_change")
check_cmdstan_toolchain()

set_cmdstan_path()

cmdstan_path()
```
# Simulated Data

Create a sample with neuroticism scores (normal distributed)

```{r}
set.seed(040519)

n <- 200
days_per_person <- 30
n_days <- n*days_per_person

people <- tibble(
  id = 1:n,
  neurot = rnorm(n), 
  latentaffect = rnorm(n), 
  latentaffectsd = rnorm(n), 
  
)
sd(people$neurot)

```

This is how we simulate measurement.
censored from 1-5

```{r cars}
measure <- function(x) {
  x[x < -2] <- -2
  x[x > 2] <- 2
  round(x,1) +3
}
```

## 3 true models 
True model 1: Associations with the mean (diary1)
True model 2: Associations with SD (diary2)
True model 3: Both (diary3)

```{r}

diary1 <-  people %>% full_join(
   tibble(
     id = rep(1:n, each = days_per_person),
   ), by = 'id') %>%
   mutate(
     Aff1 =  -1.4 + 0.5* neurot + 0.3* latentaffect +
        rnorm(n_days, mean =0 , sd = exp(-1.1 + 0 * neurot + 0.3* latentaffectsd))
   )

qplot(diary1$neurot, diary1$Aff1, alpha = I(0.1)) + geom_hline(yintercept = -2, linetype = "dashed")
qplot(diary1$Aff1)
qplot(measure(diary1$Aff1), binwidth = .1)
sd(diary1$Aff1[6001:9000])

diary1  %>% group_by(id, neurot)  %>% 
  summarise(Aff1 = mean(Aff1)) %>% ungroup() %>% summarise(cor(Aff1, neurot))


sd(diary1$neurot)
sd(diary1$Aff1)
hist(diary1$Aff1)
qplot(diary1$neurot, diary1$Aff1)


diary2 <-  people %>% full_join(
   tibble(
     id = rep(1:n, each = days_per_person),
   ), by = 'id') %>%
   mutate(
     Aff2 =  -1.4 + 0 * neurot + 0.3* latentaffect +
        rnorm(n_days, mean = 0, sd = exp(-1.1 +0.15 * neurot + 0.3*latentaffectsd))
   )

sd(diary2$Aff2)
qplot(diary2$Aff2)
qplot(diary2$neurot, diary2$Aff2, alpha = I(0.1)) + geom_hline(yintercept = -2, linetype = "dashed")
qplot(measure(diary2$Aff2), binwidth = .1)

diary3 <-  people %>% full_join(
   tibble(
     id = rep(1:n, each = days_per_person),
   ), by = 'id') %>%
   mutate(
     Aff3 =  -1.4 + 0.5 * neurot + 0.3*latentaffect +
        rnorm(n_days, mean = 0, sd = exp(-1.1 + 0.15 * neurot + 0.3* latentaffectsd))
   )

sd(diary3$neurot)
sd(diary3$Aff3)
qplot(diary3$neurot, diary3$Aff3, alpha = I(0.1)) + geom_hline(yintercept = -2, linetype = "dashed")
qplot(measure(diary3$Aff3), binwidth = .1)
sd(measure(diary3$Aff3), na.rm=T)
qplot(diary3$Aff3, binwidth = .1)
```

Add measured Affect to all three Simulations

```{r}
diary1 <- diary1 %>%  
  mutate(
    Affect_m =  measure(Aff1)                          
  )
sd(diary1$Affect_m)
round(cor(diary1 %>% select(Aff1, Affect_m)),2)   
qplot(diary1$Affect_m, binwidth=.1)


diary2 <- diary2 %>%  
  mutate(
    Affect_m =  measure(Aff2 )                          
  )

sd(diary2$Affect_m)
round(cor(diary2 %>% select(Aff2, Affect_m)),2)   
qplot(diary2$Affect_m, binwidth=.1)

diary3 <- diary3 %>%  
  mutate(
    Affect_m =  measure(Aff3)                          
  )
sd(diary3$Affect_m)
#round(cor(diary3 %>% select(Aff3, Affect_m)),2)   
qplot(diary3$Affect_m, binwidth=.1)
```

```{r}
diary1$Acens <- case_when(diary1$Affect_m == 1 ~ "left",
                         diary1$Affect_m == 5 ~ "right",
                         TRUE ~ "none")
table(diary1$Acens)

```

```{r}
diary2$Acens <- case_when(diary2$Affect_m == 1 ~ "left",
                         diary2$Affect_m == 5 ~ "right",
                         TRUE ~ "none")
table(diary2$Acens)


diary3$Acens <- case_when(diary3$Affect_m == 1 ~ "left",
                         diary3$Affect_m == 5 ~ "right",
                         TRUE ~ "none")
table(diary3$Acens)


```

Add measured neuroticism to all three Simulations

```{r}

measure_n <- function(x) {
  # expects that x is N(0,1)
  x <- x 
   
  round(x,1) 
}

diary1 <- diary1 %>%  
  mutate(
    neurot_m =  measure_n(neurot)                          
  )
sd(diary1$neurot_m)
#round(cor(diary1 %>% select(neurot, neurot_m)),2)   
qplot(diary1$neurot_m, binwidth=.1)


diary2 <- diary2 %>%  
  mutate(
    neurot_m =  measure_n(neurot)                          
  )
sd(diary2$neurot_m)
#round(cor(diary2 %>% select(neurot, neurot_m)),2)   
#qplot(diary2$neurot_m, binwidth=.1)


diary3 <- diary3 %>%  
  mutate(
    neurot_m =  measure_n(neurot)                          
  )
sd(diary3$neurot_m)
#round(cor(diary3 %>% select(neurot, neurot_m)),2)   
#qplot(diary3$neurot_m, binwidth=.1)


```

# Estimated models: default priors vs. normally distributed priors 


## Simulation 1 (effect on mean)

```{r message=TRUE, warning=TRUE}
prior1 <- c(prior("normal(0,1)", class = "b"),
            prior("normal(0,1)", class = "b", dpar = "sigma"),
          prior("normal(0,1)", class = "sd"))


w1model_neuro3 <- brm(bf(Affect_m | cens(Acens) ~ neurot_m + (1|id),
                       sigma ~ neurot_m + (1|id)), data = diary1,
                    iter = 6000, warmup = 2000, init = 0.1,
                    file = "w1model_neuro3")

w1m3_prior <- brm(bf(Affect_m | cens(Acens) ~ neurot_m + (1|id),
                       sigma ~ neurot_m + (1|id)), data = diary1,
                      prior = prior1,init = 0.1,
                    iter = 6000, warmup = 2000, 
                    file = "w1m3prior")

prior_summary(w1m3_prior)
print(w1m3_prior)

print(w1model_neuro3)
plot(w1model_neuro3)

```

## Simulation 2 (effect on  SD) 

```{r message=TRUE, warning=TRUE}
w2model_neuro3 <- brm(bf(Affect_m | cens(Acens) ~ neurot_m + (1|id),
                    sigma ~ neurot_m + (1|id)), data = diary2,
                    control = list(adapt_delta = .99),chains = 8,
                    iter = 6000, warmup = 2000, init = 0.1,
                   file = "w2model_neuro3")
print(w2model_neuro3)
#plot(w2model_neuro3)

w2m3_prior <- brm(bf(Affect_m | cens(Acens) ~ neurot_m + (1|id),
                       sigma ~ neurot_m + (1|id)), data = diary2,
                      prior = prior1,init = 0.1,
                    iter = 6000, warmup = 2000, 
                    file = "w2m3prior")

prior_summary(w2m3_prior)
print(w2m3_prior)
```

## Simulation 3 (effects on both)

```{r message=TRUE, warning=TRUE}
w3model_neuro3 <- brm(bf(Affect_m| cens(Acens)  ~ neurot_m + (1|id),
                       sigma ~ neurot_m + (1|id)), data = diary3,
                      iter = 7000, warmup = 2000,chains = 8,
                    control = list(adapt_delta = .99), inits = 0.1 ,        #options = list(adapt_delta = 0.99)
                   file = "w3model_neuro3")
print(w3model_neuro3)

w3m3_prior <- brm(bf(Affect_m | cens(Acens) ~ neurot_m + (1|id),
                       sigma ~ neurot_m + (1|id)), data = diary3,
                      prior = prior1,init = 0.1,
                    iter = 6000, warmup = 2000, 
                    file = "w3m3prior")

prior_summary(w3m3_prior)
print(w3m3_prior)
#plot(w3model_neuro3)
#qplot(diary3$neurot_m, diary3$Affect_m, alpha = I(0.1))
```



