---
title: "Additional Simulation with Skewed Normal Distribution"
output:
  html_document: 
    toc: yes
    number_sections: yes
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidybayes)
library(psych)
library(distributional)
library(ggdist )
#install.packages("~/rstudio01/Neu/relativeVariability_1.0.tar.gz", repos = NULL, type = "source")
library(relativeVariability)
library(brms)
library(cmdstanr)

#rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())

getwd()
setwd("/home/sc.uni-leipzig.de/no628luhi/ADDsim")
#run parallel cores 
options(mc.cores = parallel::detectCores(), brms.backend = "cmdstanr", brms.file_refit = "on_change")
check_cmdstan_toolchain()
set_cmdstan_path()
cmdstan_path()

```

# Simulate Skewed Data

latentaffect as skewed 

```{r}
set.seed(0405191)

n <- 200
days_per_person <- 30
n_days <- n*days_per_person

people <- tibble(
  id = 1:n,
  neurot = rnorm(n), 
  latentaffect = brms::rskew_normal(n, alpha = 100), 
  latentaffectsd =rnorm(n), 
  
)
sd(people$neurot)

qplot(people$latentaffect, binwidth= 0.1)

```

Measure Function 
no Error, cuts off skewed distribution (since these do not have their own minimum value)

```{r cars}
measure <- function(x) {
  x[x < 0] <- 0
  x[x > 4] <- 4
  round(x,1) +1
}
```

## 3 true models 
True model 1: Associations with the mean (diary4)
True model 2: Associations with SD (diary5)
True model 3: Both (diary6)

```{r}
diary4 <-  people %>% full_join(
   tibble(
     id = rep(1:n, each = days_per_person),
   ), by = 'id') %>%
   mutate(
     Aff1 =  brms::rskew_normal(n = n_days, xi = 0.1 + 0.3* neurot + 0.3* latentaffect, sigma = exp(-0.6 + 0 * neurot + 0.3* latentaffectsd), alpha = 10)
   )

qplot(diary4$Aff1,  binwidth = .1)
qplot(measure(diary4$Aff1), binwidth = .1)

diary4  %>% group_by(id, neurot)  %>% 
  summarise(Aff1 = mean(Aff1)) %>% ungroup() %>% summarise(cor(Aff1, neurot))


sd(diary4$neurot)
sd(diary4$Aff1)
hist(diary4$Aff1)
qplot(diary4$neurot, diary4$Aff1)


diary5 <-  people %>% full_join(
   tibble(
     id = rep(1:n, each = days_per_person),
   ), by = 'id') %>%
   mutate(
     Aff2 =brms::rskew_normal(n = n_days, xi = 0.1 + 0* neurot + 0.3* latentaffect, sigma = exp(-.8 + 0.15 * neurot + 0.3* latentaffectsd), alpha = 10)
   )
       
sd(diary5$Aff2)
qplot(diary5$Aff2)
qplot(diary5$neurot, diary5$Aff2, alpha = I(0.1)) + geom_hline(yintercept = -2, linetype = "dashed")
qplot(measure(diary5$Aff2), binwidth = .1)

diary6 <-  people %>% full_join(
   tibble(
     id = rep(1:n, each = days_per_person),
   ), by = 'id') %>%
   mutate(
      Aff3 =brms::rskew_normal(n = n_days, xi =0.3+ 0.3*neurot + 0.3*latentaffect, sigma = exp(-.8 + 0.15 * neurot + 0.3*latentaffectsd), alpha = 10)
   )

qplot(diary6$Aff3, binwidth = .1)
qplot(measure(diary6$Aff3), binwidth = .1)


sd(diary6$neurot)
sd(diary6$Aff3)
qplot(diary6$neurot, diary6$Aff3, alpha = I(0.1)) + geom_hline(yintercept = -2, linetype = "dashed")
```

Add measured Affect to all three Simulations

```{r}
diary4 <- diary4 %>%  
  mutate(
    Affect_m =  measure(Aff1)                          
  )
sd(diary4$Affect_m)
round(cor(diary4 %>% select(Aff1, Affect_m)),2)   
qplot(diary4$Affect_m, binwidth=.1)


diary5 <- diary5 %>%  
  mutate(
    Affect_m =  measure(Aff2 )                          
  )

sd(diary5$Affect_m)
round(cor(diary5 %>% select(Aff2, Affect_m)),2)   
qplot(diary5$Affect_m, binwidth=.1)

diary6 <- diary6 %>%  
  mutate(
    Affect_m =  measure(Aff3)                          
  )
sd(diary6$Affect_m)
#round(cor(diary6 %>% select(Aff3, Affect_m)),2)   
qplot(diary6$Affect_m, binwidth=.1)
```

```{r}
diary4$Acens <- case_when(diary4$Affect_m == 1 ~ "left",
                         diary4$Affect_m == 5 ~ "right",
                         TRUE ~ "none")
table(diary4$Acens)

diary5$Acens <- case_when(diary5$Affect_m == 1 ~ "left",
                         diary5$Affect_m == 5 ~ "right",
                         TRUE ~ "none")
table(diary5$Acens)


diary6$Acens <- case_when(diary6$Affect_m == 1 ~ "left",
                         diary6$Affect_m == 5 ~ "right",
                         TRUE ~ "none")
table(diary6$Acens)


```

Add measured neuroticism to all three Simulations

```{r}

measure_n <- function(x) {
  # expects that x is N(0,1)
  x <- x 
   
  round(x,1) 
}

diary4 <- diary4 %>%  
  mutate(
    neurot_m =  measure_n(neurot)                          
  )
sd(diary4$neurot_m)
#round(cor(diary4 %>% select(neurot, neurot_m)),2)   
qplot(diary4$neurot_m, binwidth=.1)


diary5 <- diary5 %>%  
  mutate(
    neurot_m =  measure_n(neurot)                          
  )
sd(diary5$neurot_m)
#round(cor(diary5 %>% select(neurot, neurot_m)),2)   
#qplot(diary5$neurot_m, binwidth=.1)


diary6 <- diary6 %>%  
  mutate(
    neurot_m =  measure_n(neurot)                          
  )
sd(diary6$neurot_m)
#round(cor(diary6 %>% select(neurot, neurot_m)),2)   
#qplot(diary6$neurot_m, binwidth=.1)


```

# Estimated models

model 1: naiv: only associations with the mean, normal distribution assumption
model 2: associations with the mean, censored
model 3: association with mean and variability, censored

## Simulation 4 (effect on mean)

```{r message=TRUE, warning=TRUE}

w4model_neuro3 <- brm(bf(Affect_m | cens(Acens) ~ neurot_m + (1|id),
                       sigma ~ neurot_m + (1|id)), data = diary4,
                    iter = 6000, warmup = 2000, init = 0.1,
                    file = "w4skew")
print(w4model_neuro3)
plot(w4model_neuro3)
prior_summary(w4model_neuro3)

```

## Simulation 5 (effect on  SD) 

```{r message=TRUE, warning=TRUE}
w5model_neuro3 <- brm(bf(Affect_m | cens(Acens) ~ neurot_m + (1|id),
                    sigma ~ neurot_m + (1|id)), data = diary5,
                    control = list(adapt_delta = .99),chains = 4,
                    iter = 6000, warmup = 2000, init = 0.1,
                   file = "w5skew")
print(w5model_neuro3)
prior_summary(w5model_neuro3)


plot(w5model_neuro3)
```

## Simulation 6 (effects on both)

```{r message=TRUE, warning=TRUE}
w6model_neuro3 <- brm(bf(Affect_m| cens(Acens)  ~ neurot_m + (1|id),
                       sigma ~ neurot_m + (1|id)), data = diary6,
                      iter = 7000, warmup = 2000,chains = 4,
                    control = list(adapt_delta = .99), inits = 0.1 ,        #options = list(adapt_delta = 0.99)
                   file = "w6skew")
print(w6model_neuro3)
plot(w6model_neuro3)
prior_summary(w6model_neuro3)

```

# Results

```{r}
extract_param2 <- function(model, parameter) {
  ci <- posterior_summary(model, variable = parameter)
  est <- sprintf("%.4f %.4f %.4f", ci[,"Estimate"], ci[,"Q2.5"], ci[,"Q97.5"])
  est
}

results_sim <- data.frame(matrix(nrow = 7, # Modelle & RVI 
                             ncol = 9+1)) # 3 Wahre Welten a 3 Spalten 
names(results_sim) <- c("model", "w4_b_neuro", "w4_b_neuro_sigma", "w4_sigma",
                    "w5_b_neuro", "w5_b_neuro_sigma", "w5_sigma",
                    "w6_b_neuro", "w6_b_neuro_sigma", "w6_sigma"
                    )

results_sim$model <- c("model1", "model2", "model3",
                  "RVI", "RVI_weight", "SD", "SD*")



#summary(w4model_neuro)$fixed
#posterior_summary(w4model_neuro3)
```

```{r}
results_sim[3, "w4_b_neuro"] <- extract_param2(w4model_neuro3, "b_neurot_m")
results_sim[3, "w4_b_neuro_sigma"] <- extract_param2(w4model_neuro3, "b_sigma_neurot_m")
results_sim[3, "w4_sigma"] <- extract_param2(w4model_neuro3, "b_sigma_Intercept")
```

```{r}
results_sim[3, "w5_b_neuro"] <- extract_param2(w5model_neuro3, "b_neurot_m")
results_sim[3, "w5_b_neuro_sigma"] <- extract_param2(w5model_neuro3, "b_sigma_neurot_m")
results_sim[3, "w5_sigma"] <- extract_param2(w5model_neuro3, "b_sigma_Intercept")
```

```{r}
results_sim[3, "w6_b_neuro"] <- extract_param2(w6model_neuro3, "b_neurot_m")
results_sim[3, "w6_b_neuro_sigma"] <- extract_param2(w6model_neuro3, "b_sigma_neurot_m")
results_sim[3, "w6_sigma"] <- extract_param2(w6model_neuro3, "b_sigma_Intercept")

```

# RVI (Relative-Variability-Index) 
## Unweighted RVI for all three Simulations

```{r}
people <- people %>%  
  mutate(
    neurot =  measure_n(neurot)                          
  )

id <- unique(diary4$id)
id <- as.data.frame(id)

people$RSD_d4 <- NA
for (i in 1:nrow(id)) {
  if (id$id[i] %in% diary4$id) {
      people$RSD_d4[i] <- relativeSD(diary4$Affect_m[diary4$id == id$id[i]],
                                         1, 5)
    }
  } 


people$logrsd_d4 <- log(people$RSD_d4)

m_rsd_d4 <- brm(logrsd_d4 ~ neurot, data= people)
print(m_rsd_d4, digits=4)

results_sim[4,3] <- extract_param2(m_rsd_d4, "b_neurot")
 
people$RSD_d5 <- NA
for (i in 1:nrow(id)) {
  if (id$id[i] %in% diary5$id) {
      people$RSD_d5[i] <- relativeSD(diary5$Affect_m[diary5$id == id$id[i]],
                                         1, 5)
    }
  } 

people$logrsd_d5 <- log(people$RSD_d5)

m_rsd_d5 <- brm( logrsd_d5~ neurot, data= people)
m_rsd_d5
results_sim[4,6] <- extract_param2(m_rsd_d5, "b_neurot")

people$RSD_d6 <- NA
for (i in 1:nrow(id)) {
  if (id$id[i] %in% diary6$id) {
      people$RSD_d6[i] <- relativeSD(diary6$Affect_m[diary6$id == id$id[i]],
                                         1, 5)
    }
  } 

people$logrsd_d6 <- log(people$RSD_d6)

m_rsd_d6 <- brm(logrsd_d6 ~ neurot, data= people)
m_rsd_d6
results_sim[4,9] <- extract_param2(m_rsd_d6, "b_neurot")


```

## weighted RVI for all three Simulations 

```{r}
people$mean_Aff_d4 <- NA
for (i in 1:nrow(id)) {
  if (id$id[i] %in% diary4$id) {
      people$mean_Aff_d4[i] <- mean(diary4$Affect_m[diary4$id == id$id[i]],
                                   na.rm = T)
    }
  } 

range(people$mean_Aff_d4)

people$mean_Aff_d5 <- NA
for (i in 1:nrow(id)) {
  if (id$id[i] %in% diary5$id) {
      people$mean_Aff_d5[i] <- mean(diary5$Affect_m[diary5$id == id$id[i]],
                                   na.rm = T)
    }
  } 

range(people$mean_Aff_d5)


people$mean_Aff_d6 <- NA
for (i in 1:nrow(id)) {
  if (id$id[i] %in% diary6$id) {
      people$mean_Aff_d6[i] <- mean(diary6$Affect_m[diary6$id == id$id[i]],
                                   na.rm = T)
    }
  } 

range(people$mean_Aff_d6)

```


```{r}
people$weight_d4 <- NA
for (i in 1:nrow(id)) {
  if (id$id[i] %in% diary4$id) {
      people$weight_d4[i] <- maximumSD(people$mean_Aff_d4[i], 
                                       1,  # Minimum
                                       5,  # Maximum
                                       sum(!is.na(diary4$Affect_m[diary4$id == id$id[i]])) # Anzahl Beobachtungen in var eingeflossen/30
      ) 
      # W as reported in paper
      people$weight_d4[i] <- people$weight_d4[i]^2
    }
}

people$weight_d5 <- NA
for (i in 1:nrow(id)) {
  if (id$id[i] %in% diary5$id) {
      people$weight_d5[i] <- maximumSD(people$mean_Aff_d5[i], 
                                       1,  # Minimum
                                       5,  # Maximum
                                       sum(!is.na(diary5$Affect_m[diary5$id == id$id[i]])) # Anzahl Beobachtungen in var eingeflossen/30
      ) 
      # W as reported in paper
      people$weight_d5[i] <- people$weight_d5[i]^2
    }
}

people$weight_d6 <- NA
for (i in 1:nrow(id)) {
  if (id$id[i] %in% diary6$id) {
      people$weight_d6[i] <- maximumSD(people$mean_Aff_d6[i], 
                                       1,  # Minimum
                                       5,  # Maximum
                                       sum(!is.na(diary6$Affect_m[diary6$id == id$id[i]])) # Anzahl Beobachtungen in var eingeflossen/30
      ) 
      # W as reported in paper
      people$weight_d6[i] <- people$weight_d6[i]^2
    }
}

```


```{r}
m_rsd_d4_w <- brm(logrsd_d4| weights(weight_d4) ~ neurot, data= people)
m_rsd_d4_w
results_sim[5,3] <- extract_param2(m_rsd_d4_w, "b_neurot")

m_rsd_d5_w <- brm(logrsd_d5| weights(weight_d5) ~ neurot, data= people)
m_rsd_d5_w
results_sim[5,6] <- extract_param2(m_rsd_d5_w, "b_neurot")

m_rsd_d6_w <- brm(logrsd_d6| weights(weight_d6) ~ neurot, data= people)
m_rsd_d6_w
results_sim[5,9] <- extract_param2(m_rsd_d6_w, "b_neurot")
```

# SD

```{r}
people$sd_Aff_d4 <- NA
for (i in 1:nrow(id)) {
  if (id$id[i] %in% diary4$id) {
      people$sd_Aff_d4[i] <- sd(diary4$Affect_m[diary4$id == id$id[i]],
                                   na.rm = T)
    }
}

people$sd_Aff_d5 <- NA
for (i in 1:nrow(id)) {
  if (id$id[i] %in% diary5$id) {
      people$sd_Aff_d5[i] <- sd(diary5$Affect_m[diary5$id == id$id[i]],
                                   na.rm = T)
    }
}

people$sd_Aff_d6 <- NA
for (i in 1:nrow(id)) {
  if (id$id[i] %in% diary6$id) {
      people$sd_Aff_d6[i] <- sd(diary6$Affect_m[diary6$id == id$id[i]],
                                   na.rm = T)
    }
}

people$sd_Aff_d4[people$sd_Aff_d4 == 0] <- NA   
people$sd_Aff_d5[people$sd_Aff_d5 == 0] <- NA   
people$sd_Aff_d6[people$sd_Aff_d6 == 0] <- NA   

people$logsd_d4 <- log(people$sd_Aff_d4)
people$logsd_d5 <- log(people$sd_Aff_d5)
people$logsd_d6 <- log(people$sd_Aff_d6)




mean(people$sd_Aff_d4)  
mean(people$sd_Aff_d5)  
mean(people$sd_Aff_d6, na.rm = T)  
```

## Regression with SD

```{r}

m_sd_d4 <- brm(logsd_d4 ~ neurot, data= people, file = "logsd_d4")
m_sd_d4
results_sim[6,3] <- extract_param2(m_sd_d4, "b_neurot")


m_sd_d5 <- brm(logsd_d5 ~ neurot, data= people, file = "logsd_d5")
m_sd_d5
results_sim[6,6] <- extract_param2(m_sd_d5, "b_neurot")

m_sd_d6 <- brm(logsd_d6 ~ neurot, data= people, file = "logsd_d6")
m_sd_d6
results_sim[6,9] <- extract_param2(m_sd_d6, "b_neurot")

```

## Regression with SD + controlling for mean values of negative Emotion 

```{r}

m_sd_d4c <- brm(logsd_d4 ~ neurot + mean_Aff_d4, data= people)
m_sd_d4c
results_sim[7,3] <- extract_param2(m_sd_d4c, "b_neurot")


m_sd_d5c <- brm(logsd_d5 ~ neurot + mean_Aff_d5, data= people)
m_sd_d5c
results_sim[7,6] <- extract_param2(m_sd_d5c, "b_neurot")

m_sd_d6c <- brm(logsd_d6 ~ neurot + mean_Aff_d6, data= people)
m_sd_d6c
results_sim[7,9] <- extract_param2(m_sd_d6c, "b_neurot")

```


```{r}
results_sim

library("writexl")
write_xlsx(results_sim,"results_sim2.xlsx")
```

# Plot Simulaion 

```{r}
apatheme = theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        panel.border = element_blank(),
        text=element_text(family='Arial'),
        legend.title=element_blank(),
        legend.position=c(.7,.8),
        axis.line.x = element_line(color='black'),
        axis.line.y = element_line(color='black'))

#getwd()

#results_sim <- read_xlsx("~/results_sim2.xlsx")
results_sim2 <- results_sim 

results_sim2$w4_sigma <- NULL
results_sim2$w5_sigma <- NULL
results_sim2$w6_sigma <- NULL


results_sim2 <- results_sim2 %>% 
  tidyr::separate(w4_b_neuro_sigma,                      
                  c("w4_b_neuro_sigma","lowerw4", "upperw4"), sep = " ")


results_sim2 <- results_sim2 %>% 
  tidyr::separate(w5_b_neuro_sigma,                      
                  c("w5_b_neuro_sigma", "lowerw5", "upperw5"), sep = " ")


results_sim2 <- results_sim2 %>% 
  tidyr::separate(w6_b_neuro_sigma,                      
                  c("w6_b_neuro_sigma", "lowerw6", "upperw6"), sep = " ")


resultsw4sig <- results_sim2
resultsw4sig <- resultsw4sig[-c(1,2), ]
resultsw4sig <- resultsw4sig[-6, ]
resultsw4sig[1,1] <- "BCLSM"
resultsw4sig[3,1] <- "weighted RVI"


resultsw4sig$w4_b_neuro_sigma <- as.numeric(resultsw4sig$w4_b_neuro_sigma )
resultsw4sig$w5_b_neuro_sigma <- as.numeric(resultsw4sig$w5_b_neuro_sigma )
resultsw4sig$w6_b_neuro_sigma <- as.numeric(resultsw4sig$w6_b_neuro_sigma )

resultsw4sig$lowerw4 <- as.numeric(resultsw4sig$lowerw4 )
resultsw4sig$upperw4 <- as.numeric(resultsw4sig$upperw4 )

resultsw4sig$lowerw5 <- as.numeric(resultsw4sig$lowerw5 )
resultsw4sig$upperw5 <- as.numeric(resultsw4sig$upperw5 )

resultsw4sig$lowerw6 <- as.numeric(resultsw4sig$lowerw6 )
resultsw4sig$upperw6 <- as.numeric(resultsw4sig$upperw6 )

resultsw4sig$model <- as.character(resultsw4sig$model)
resultsw4sig$model <- factor(resultsw4sig$model, levels=unique(resultsw4sig$model))


w4sig <- ggplot(resultsw4sig, aes(x=model , y = w4_b_neuro_sigma))+ geom_point() +
  geom_hline(yintercept=0, linetype='dotted', col = 'black') +
  labs(x = " Statistical Approach", y = "b estimates")+ ggtitle("Negative Emotion")

w4sig+apatheme + geom_errorbar(aes(ymin = lowerw4, ymax = upperw4), width = 0.2)+coord_cartesian(ylim = c(-0.40, 0.5))+theme(plot.title = element_text(hjust = 0.5))

ggsave("w4skew.png", width = 4, height = 3)


w5sig <- ggplot(resultsw4sig, aes(x=model , y = w5_b_neuro_sigma))+ geom_point() +
  geom_hline(yintercept= 0.15, linetype='dotted', col = 'black') +
  labs(x = "Statistical Approach", y = "b estimates") + geom_errorbar(aes(ymin = lowerw5, ymax = upperw5), width = 0.2)+ ggtitle("Negative Emotion")

w5sig + apatheme +coord_cartesian(ylim = c(-0.20, 0.4))+theme(plot.title = element_text(hjust = 0.5))

ggsave("w5skew.png", width = 4, height = 3)

w6sig <- ggplot(resultsw4sig, aes(x=model , y = w6_b_neuro_sigma))+ geom_point() +
  geom_hline(yintercept= 0.15, linetype='dotted', col = 'black') +
  labs(x = "Statistical Approach", y = "b estimates") + geom_errorbar(aes(ymin = lowerw6, ymax = upperw6), width = 0.2)+ ggtitle("Negative Emotion")

w6sig + apatheme +coord_cartesian(ylim = c(-0.30, 0.5))+theme(plot.title = element_text(hjust = 0.5))

ggsave("w6skew.png", width = 4, height = 3)
```


